### 2024-11-26 paper/paper.qmd
1. construct model 2. Introduction of paper 3. remove unused file 4. remove unused package

---
title: "Focasting The Trend of Vehicle Related Crime In Calgary In 2025"
subtitle: "An Analysis of Calgary's Crime Count From 2018 to 2024"
author: 
  - Haobo Ren
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: 23-November-2024
date-format: long
abstract: "Vehicle-related crime is a long-standing challenge to urban security, so accurate prediction is necessary to effectively allocate police resources and develop security policies. This study examines trends in vehicle-related crime in Calgary, Canada, focusing on two types of crime: Theft of vehicle and Theft from vehicle. A Bayesian regression model is fit to historical crime data from January 2018 to October 2024, accounting for seasonal variations (months), long-term trends (years), and differences between crime categories. The usefulness of Bayesian modeling for crime trend forecasting is demonstrated by this analysis, providing law enforcement and policymakers practical insights to foresee and handle long-term and seasonal crime trends."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

```

# Introduction

Urban crime is an ongoing problem compromising public confidence, economic stability, and safety. Among the several types of crimes, vehicle-related offenses include theft of vehicles and theft from vehicles remain a major issue in urban areas across the country. These crimes disturb people's life but also burden local governments and law enforcement. Over the years, Calgary, Canada, has seen varying patterns in vehicle-related crimes, which raises issues regarding future developments of these trends. Designing effective preventive plans, maximizing resource allocation, and guaranteeing community safety all depend on an awareness of current trends and future crime count prediction. This study forecasts vehicle-related crime patterns in Calgary up until 2025, therefore addressing these issues.

Analyzing and projecting monthly crime counts for theft from vehicles and theft of vehicles in Calgary is the main goal of this study. I created a Bayesian regression model to assess the effects of time (year and month) and crime category on reported crime counts using historical data spanning January 2018 through October 2024. Offering a comprehensive knowledge of how vehicle-related crimes have developed and may continue to alter in the near future, the model catches both long-term patterns and seasonal changes. The research also offers category-specific forecasts, therefore stressing variations in the seasonal and temporal trends of theft from and of vehicles.

The analysis reveals a continued decline in vehicle-related crimes in Calgary, with a mean change of -60.5 each year, and notable mean differences of -454.8 between the two categories. Theft from vehicles is anticipated to show cyclical surges in the summer months, indicating possible opportunistic habits. Conversely, vehicle theft exhibits a more stable decline throughout the course of the year. The data indicate that, although overall vehicle-related crimes are down, seasonal surges in certain categories persist as a problem for policymakers and law enforcement to tackle.

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-26 scripts/00-simulate_data.R

@@ -8,7 +8,6 @@
 
 #### Workspace setup ####
 library(dplyr)
-library(tidyverse)
 
 #### Simulate data ####
 # Set seed for reproducibility

### 2024-11-26 scripts/03-clean_data.R

@@ -7,10 +7,9 @@
 
 
 #### Workspace setup ####
-library(tidyverse)
 library(dplyr)
 library(janitor)
-library(zoo)
+library(arrow)
 
 #### Clean data ####
 raw_data <- read_csv("data/01-raw_data/raw_data.csv")
@@ -18,10 +17,11 @@ raw_data <- read_csv("data/01-raw_data/raw_data.csv")
 cleaned_data <- raw_data %>% clean_names() %>%
   group_by(category, year, month) %>%
   summarise(crime_count = sum(crime_count), .groups = "drop") %>%
-  mutate(time = paste0(year, "-", sprintf("%02d", month))) %>%
-  select(category, crime_count, time) %>% arrange(category,time)
+  mutate(time = as.Date(paste0(year, "-", sprintf("%02d", month), "-01"))) %>%
+  select(category, crime_count, year, month, time) %>% arrange(category, year, month) %>%
+  filter(category == "Theft OF Vehicle" | category == "Theft FROM Vehicle")
 
-cleaned_data$time <- as.yearmon(cleaned_data$time, format = "%Y-%m")
 
 #### Save data ####
-write_csv(cleaned_data, "data/02-analysis_data/analysis_data.csv")
+write_csv(cleaned_data, "data/02-analysis_data/calgory_crime.csv")
+write_parquet(cleaned_data, "data/02-analysis_data/calgory_crime.parquet")

### 2024-11-26 scripts/04-test_analysis_data.R

@@ -11,10 +11,22 @@
 #### Workspace setup ####
 library(tidyverse)
 
-analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
+analysis_data <- read_csv("data/02-analysis_data/calgory_crime.csv")
 
 
 #### Test data ####
-# Test that the dataset has total of 212950 crime counts
-crime_counts
 
+# Test that the dataset has no na
+any_na <- any(is.na(analysis_data))
+if (any_na) {
+  print("The dataset contains NA values.")
+} else {
+  print("The dataset does not contain any NA values.")
+}
+
+# Check if months are valid
+if (all(analysis_data$month >= 1 & analysis_data$month <= 12)) {
+  print("All months are within the valid range (1-12).")
+} else {
+  print("Some months are out of the valid range (1-12).")
+}

### 2024-11-26 scripts/05-model_data.R

@@ -1,0 +1,80 @@
+#### Preamble ####
+# Purpose: Model the trend of total number of crimes for each category in Calgary
+# Author: Haobo Ren
+# Date: 23 November 2024
+# Contact: haobo.ren@mail.utoronto.ca
+# Pre-requisites: ensure data file is available in the specified directory
+
+
+#### Workspace setup ####
+library(rstanarm)
+library(arrow)
+library(ggplot2)
+
+#### Read data ####
+crime_data <- read_parquet("data/02-analysis_data/calgory_crime.parquet")
+
+### Model data ####
+
+# Ensure `category` is treated as a factor
+crime_data$category <- as.factor(crime_data$category)
+crime_data$month <- as.factor(crime_data$month)
+
+
+# Fit a Bayesian regression model
+crime_model <- stan_glm(
+  formula = crime_count ~ year + month + category + category:month + category:year,
+  data = crime_data,
+  family = gaussian(),
+  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  prior_aux = exponential(rate = 1, autoscale = TRUE),
+  seed = 369
+)
+
+
+### Visualize Data
+
+# Construct fitted value data
+fitted_data <- expand.grid(
+  year = 2018:2025,
+  month = 1:12,
+  category = c("Theft FROM Vehicle", "Theft OF Vehicle")
+) %>%
+  mutate(
+    time = as.Date(paste(year, month, "01", sep = "-")), # Create time range
+    month = as.factor(month),
+    category = as.factor(category)
+  )
+
+# Predict crime counts using the model
+fitted_data$fitted_crime_count <- predict(crime_model, newdata = fitted_data)
+
+# Visualize trends
+crime_data$source <- "Actual"
+fitted_data$source <- "Fitted"
+combined_data <- bind_rows(
+  crime_data %>% select(time, crime_count, category, source),
+  fitted_data %>% rename(crime_count = fitted_crime_count) %>% select(time, crime_count, category, source)
+)
+
+# Plot combined trends
+ggplot(combined_data, aes(x = time, y = crime_count, color = category, linetype = source)) +
+  geom_line() +
+  labs(
+    title = "Actual vs. Fitted Crime Trends (2018-2025)",
+    x = "Time",
+    y = "Crime Count",
+    color = "Category",
[…]

### 2024-11-26 scripts/06-model_data.R

@@ -1,51 +1,0 @@
-#### Preamble ####
-# Purpose: Model the trend of total number of crimes for each category in Calgary
-# Author: Haobo Ren
-# Date: 23 November 2024
-# Contact: haobo.ren@mail.utoronto.ca
-# Pre-requisites: ensure data file is available in the specified directory
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-library(arrow)
-
-#### Read data ####
-crime_data <- read_parquet("data/02-analysis_data/calgory_crime.parquet")
-
-### Model data ####
-
-
-# Fit a Bayesian regression model
-crime_model <- stan_glm(
-  formula = crime_count ~ time + category,
-  data = crime_data,
-  family = gaussian(),
-  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-  prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-  prior_aux = exponential(rate = 1, autoscale = TRUE),
-  seed = 853
-)
-
-# Visualize trends
-crime_data %>%
-  ggplot(aes(x = time, y = crime_count, color = category)) +
-  geom_line() +
-  labs(
-    title = "Trend of Total Crimes by Category Over Time",
-    x = "Year-Month",
-    y = "Total Crimes",
-    color = "Category"
-  ) +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-summary(crime_model)
-#### Save model ####
-saveRDS(
-  crime_model,
-  file = "models/first_model.rds"
-)
-
-

### 2024-11-26 paper/paper.qmd
revise the introduction section

@@
 
-Analyzing and projecting monthly crime counts for theft from vehicles and theft of vehicles in Calgary is the main goal of this study.
+Analyzing and projecting monthly crime counts for theft from vehicles and theft of vehicles in Calgary is the estimand of this study.
 I created a Bayesian regression model to assess the effects of time (year and month) and crime category on reported crime counts using historical data spanning January 2018 through October 2024.
@@
 Conversely, vehicle theft exhibits a more stable decline throughout the course of the year.
-The data indicate that, although overall vehicle-related crimes are down, seasonal surges in certain categories persist as a problem for policymakers and law enforcement to tackle.
+The data indicate that, although overall vehicle-related crimes are down, seasonal surges in certain categories persist as a problem for policymakers and law enforcement to tackle, for example, the crime count of Theft From Vehicle in August is expected larger than January by 159.4.
 
-Why it matters paragraph
+The study is significant for its role in proactive crime prevention and resource optimization.
+This study offers precise and comprehensible forecasts, providing policymakers and law enforcement with evidence-based insights to inform decision-making.
+This study addresses a significant research gap and enhances public safety in Calgary.
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+#Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+
+The data analysis and visualization is done in R[@citeR] with the following Packages:
 

### 2024-11-26 scripts/00-simulate_data.R
Romove unused package

@@ -7,7 +7,7 @@
 
 
 #### Workspace setup ####
-library(dplyr)
+library(tidyverse)
 
 #### Simulate data ####
 # Set seed for reproducibility

### 2024-11-26 scripts/03-clean_data.R

@@ -7,7 +7,7 @@
 
 
 #### Workspace setup ####
-library(dplyr)
+library(tidyverse)
 library(janitor)
 library(arrow)
 

### 2024-11-26 scripts/05-model_data.R

@@ -10,6 +10,7 @@
 library(rstanarm)
 library(arrow)
 library(ggplot2)
+library(dplyr)
 
 #### Read data ####
 crime_data <- read_parquet("data/02-analysis_data/calgory_crime.parquet")

### 2024-11-26 paper/paper.qmd
Edit data section and references.bib

@@
   - Haobo Ren
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
+thanks: "Code and data are available at: https://github.com/HaoboRrrr/calgary_vehicle_crime_forcast"
 date: 23-November-2024
@@
 library(tidyverse)
+library(here)
+library(knitr)
 
@@
 
-The data analysis and visualization is done in R[@citeR] with the following Packages:
-
 # Data {#sec-data}
@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+The raw dataset obtained from Open Data Calgary[@OpenCalgary] was recorded and updated monthly by the Calgary Police Service.
+The data is considered cumulative as late-reported incidents are often received well after an offence has occurred.
+An incident is either reported just after the crime happened, or reported on the Calgary Police Service[@calgarypolice].
 
-Overview text
+The data analysis and visualization is done in R[@citeR] with the following Packages: tidyverse[@tidy], janitor[@janitor], arrow[@arrow], rstanarm[@rstanarm], ggplot2[@ggplot2], dplyr[@dplyr], here, knitr.
 
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+The data reflects reported crime incidents across Calgary, categorized by community, crime type, and temporal details (year and month).
+Each row in the dataset represents a summary of crime counts for a specific category and community within a given month and year.
+The Calgary Police Service serves as the primary source, systematically recording incidents reported by the public.
+These reports may be filed in several ways, including: immediate Reporting and delayed Reporting.
 
-## Outcome variables
+Crime count quantifies the number of reported incidents of a specific crime and time period and is based on the most serious violation per incident.
+The count represents and aggregation of individual reports collected by the Calgary Police Services.
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
+There are limitations in these measurement.
+Reporting Bias: Not all crimes are reported.
+Minor incidents or those involving uninsured vehicles may go unreported, leading to underestimation of true crime rates.
+Cumulative Nature: The inclusion of late-reported incidents makes it challenging to distinguish between crimes that occurred during the reported month versus those that occurred earlier.
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+By understanding how this dataset measures real-world crime phenomena, we can more confidently interpret the insights and predictions derived from it.
+
+## Data Examination {#sec-dataexam}
+
+The raw data from Open Data has five columns and 75,595 rows, the column names are displayed below:
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
 #| echo: false
+#| warning: false
+raw_data <- read_csv(here("data/01-raw_data/raw_data.csv"))
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+# Get the column names of your raw data
+column_names <- colnames(raw_data)
+
+# Convert the column names to a data frame for kable
+column_df <- as.data.frame(column_names)
+
+# Display with kable
+kable(column_df)
 ```
 
-Talk more about it.
+```{r}
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
 ```
@@
 
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
 ```
@@
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
 ```
@@
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
 ```
@@
 
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
 ```

### 2024-11-28 paper/paper.qmd
Edit paper

@@
 library(knitr)
+library(arrow)
 
+cleaned_data <- read_parquet(here("data/02-analysis_data/calgary_crime.parquet"))
 ```
@@
 
-Analyzing and projecting monthly crime counts for theft from vehicles and theft of vehicles in Calgary is the estimand of this study.
+Analyzing and projecting monthly crime counts for theft from vehicles and theft of vehicles in Calgary is the main aim of this study.
 I created a Bayesian regression model to assess the effects of time (year and month) and crime category on reported crime counts using historical data spanning January 2018 through October 2024.
@@
 ```
+- Community: The dataset is spatially disaggregated into Calgary's various communities
+
+Numeric Variable:
+
+- Year: The year of each record indicate when the incidents were reported.
+
+Categorical Variable:
+
+- Category: Each entry is categorized into distinct crime types.
+
+- month: The month of each incidents recorded. Range from 1-12 repeatedly each year
+
+Response Variable:
+
+- Crime Count: This variable quantifies the number of reported incidents of a specific crime type (e.g., theft from or of vehicles) within a given community and time period.
+
+## Data Cleaning
+
+Several steps was taken for better analysis of vehicle-related trend in Calgary.
+First, clean the names of all the columns.
+Second, the raw dataset contained granular records categorized by Community and specific details.
+These were aggregated to provide summarized counts of crimes (crime_count) by category, year, and month to align with analysis requirements.
+Third, a new time column was introduced in the cleaned data, combining year and month into a single date field (YYYY-MM-DD).
+This was essential for time-series analysis and visualization.
+Last, filter out the categories related to vehicle.
+
+## Cleaned Data
+
+The first 6 rows of the cleaned dataset are shown in @tbl-cleaned-data.
 
 ```{r}
+#| label: tbl-cleaned-data
+#| tbl-cap: Head of cleaned Calgary Crime data 
+#| echo: false
+#| warning: false
 
+kable(head(cleaned_data))
 ```
 
-Talk way more about it.
+## Response Variable
 
-## Predictor variables
+### Crime count of Theft FROM Vehicle
 
-Add graphs, tables and text.
+Summary statistics of Crime count of Theft FROM Vehicle are shown in the @tbl-response-theftfromvehicle
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+```{r}
+#| label: tbl-response-theftfromvehicle
+#| tbl-cap: Summary Statitic of crime_count(Theft FROM Vehicle)
+#| echo: false
+#| warning: false
+
+kable(cleaned_data %>% filter(category == "Theft FROM Vehicle") %>% select(crime_count) %>% summary(crime_count))
+```
+
+The response variable, crime_count, represents the number of reported incidents of theft from vehicles within Calgary.
+The summary statistics reveal a significant variability in the crime counts, ranging from a minimum of 120 to a maximum of 1,619 reported cases.
+The median value is 916, indicating that half of the recorded months experienced fewer than 916 thefts, while the other half exceeded this value.
+The mean crime count, at 932.7, is slightly higher than the median, suggesting the presence of months with particularly high crime counts that may be skewing the average.
+The interquartile range (IQR), spanning from 788.2 (1st quartile) to 1,105.5 (3rd quartile), highlights the central tendency of crime occurrences, with most months falling within this range.
+These statistics emphasize the fluctuating nature of vehicle thefts in Calgary and provide a foundational understanding for modeling and forecasting future trends.
+
+### Crime count of Theft OF Vehicle
+
+Summary statistics of Crime count of Theft FROM Vehicle are shown in the @tbl-response-theftofvehicle
+
+```{r}
+#| label: tbl-response-theftofvehicle
+#| tbl-cap: Summary Statitic of crime_count(Theft OF Vehicle)
+#| echo: false
+#| warning: false
+
+kable(cleaned_data %>% filter(category == "Theft OF Vehicle") %>% select(crime_count) %>% summary(crime_count))
+```
+
+The response variable, crime_count, for Theft OF Vehicle incidents reflects the monthly reported counts of vehicles being stolen in Calgary.
+The dataset's summary statistics indicate that the crime counts range from a minimum of 146 to a maximum of 651 incidents.
+The median count is 424.5, suggesting that half of the months have fewer than 425 thefts, while the other half exceed this value.
+Interestingly, the mean crime count is 422.5, closely aligned with the median, suggesting a relatively symmetric distribution of the data.
+The interquartile range (IQR) spans from 361.2 (1st quartile) to 469.0 (3rd quartile), indicating that most monthly counts are concentrated within this range.
+These figures highlight the scale and regularity of vehicle theft in Calgary and form an essential basis for analyzing and forecasting trends in such crimes.
+
+## Predictor Variable
+
+### year
+
+The variable year represents the timeline over which the crime data is recorded, providing insight into how vehicle-related crime counts have changed annually.
+By analyzing the data across different years, we can observe any long-term trends, such as consistent increases, decreases, or fluctuations in vehicle thefts.
+This variable helps us understand whether certain years experienced higher crime rates due to factors like economic conditions, population changes, or other external influences.
+
+### month and category
+
+The variables month and category provide a detailed view of how vehicle-related crimes are distributed across time and crime types.
+Month captures seasonal variations, showing how crime rates fluctuate throughout the year.
+For example, there might be a tendency for higher crime counts during certain seasons, such as summer or winter, influenced by weather conditions or holiday activities.
+Category distinguishes between "Theft FROM Vehicle" and "Theft OF Vehicle," allowing us to compare the frequency and patterns of these two crime types.
+Together, these variables highlight differences in the nature and timing of vehicle-related crimes, offering valuable insights into their temporal and categorical distributions.
+
+## Trend of The Two Crime
+
+The trend of Theft FROM Vehicle and Theft OF Vehicle are shown in @fig-combined-trend
+
+```{r}
+#| label: fig-combined-trend
+#| tbl-cap: Trend of The Two Crime Combined
+#| echo: false
+#| warning: false
+# Plot combined trends
+ggplot(cleaned_data, aes(x = time, y = crime_count, color = category)) +
+  geom_line() +
+  labs(
+    title = "Trend of Theft FROM Vehicle and Theft OF Vehicle",
+    x = "Time",
+    y = "Crime Count",
+    color = "Category"
+  ) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+The trends for "Theft FROM Vehicle" and "Theft OF Vehicle" reveal distinct patterns over time.
+"Theft FROM Vehicle" consistently shows higher crime counts compared to "Theft OF Vehicle," indicating that it is a more prevalent issue.
+The trend for "Theft FROM Vehicle" demonstrates significant fluctuations, with peaks around 2019 and a general decline afterward, suggesting a reduction in these incidents in more recent years.
+In contrast, "Theft OF Vehicle" exhibits a relatively stable pattern with smaller variations over time.
+Although it remains less frequent than "Theft FROM Vehicle," its counts appear to decrease gradually, particularly after 2022.
+Both categories show declining trends toward the end of the observed period, which could reflect successful crime prevention measures or other external influences.
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+The Bayesian regression model was developed to analyze and forecast the trends of vehicle-related crimes in Calgary, focusing on the categories "Theft FROM Vehicle" and "Theft OF Vehicle." The primary goal of this modeling is to understand the relationship between crime counts and key predictors such as time (year and month) and crime categories, as well as their interactions.
+By incorporating temporal and categorical variables, the model seeks to capture long-term trends, seasonal patterns, and differences between the two types of crimes.
+Ultimately, the model provides a foundation for projecting future crime rates, offering valuable insights that can support strategic decision-making and the development of targeted crime prevention initiatives for 2025 and beyond.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+The Bayesian regression model is set up to examine the relationship between vehicle-related crime counts and the selected predictors.
+The response variable, $y_i$, represents the observed crime count for the i-th observation, where each observation corresponds to a specific month, year, and crime category.
+The predictors include a numeric variable for year, categorical variables for month and category, as well as interaction terms (category:month and category:year) to capture how crime patterns differ between the two crime types over time and across seasons.
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
+The model assumes the form:
 
@@
 
-Our results are summarized in @tbl-modelresults.
+Our results are summarized in
 
@@
 #| eval: true
-#| label: tbl-modelresults
+
 #| tbl-cap: "Explanatory models of flight time based on wing width and wing length"

### 2024-11-28 paper/paper.qmd
Finish most part of paper little change to model little change to clean data

@@
 library(arrow)
+library(ggplot2)
+library(bayesplot)
 
 cleaned_data <- read_parquet(here("data/02-analysis_data/calgary_crime.parquet"))
+fitted_data <- read_parquet(here("data/02-analysis_data/fitted_calgary_crime.parquet"))
 ```
@@
 
-The analysis reveals a continued decline in vehicle-related crimes in Calgary, with a mean change of -60.5 each year, and notable mean differences of -454.8 between the two categories.
+The analysis reveals a continued decline in vehicle-related crimes in Calgary, with a mean change of -60.4 each year, and notable mean differences of -435.0 between the two categories.
 Theft from vehicles is anticipated to show cyclical surges in the summer months, indicating possible opportunistic habits.
 Conversely, vehicle theft exhibits a more stable decline throughout the course of the year.
-The data indicate that, although overall vehicle-related crimes are down, seasonal surges in certain categories persist as a problem for policymakers and law enforcement to tackle, for example, the crime count of Theft From Vehicle in August is expected larger than January by 159.4.
+The data indicate that, although overall vehicle-related crimes are down, seasonal surges in certain categories persist as a problem for policymakers and law enforcement to tackle, for example, the crime count of Theft From Vehicle in August is expected larger than January by 158.4.
 
@@
 #| label: fig-combined-trend
-#| tbl-cap: Trend of The Two Crime Combined
+#| fig-cap: Trend of The Two Crime Combined
 #| echo: false
@@
 ```
+\newpage
 
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+$$
+y_i = \beta_0 + \beta_1 \text{year}_i + \beta_2 \text{month}_i + \beta_3 \text{category}_i + \beta_4 (\text{category} \times \text{month})_i + \beta_5 (\text{category} \times \text{year})_i + \epsilon_i
+$$
 
-### Model justification
+Here, $\beta_0$ is the intercept, capturing the baseline level of crime counts.
+The coefficients $\beta_1$, $\beta_2$, and $\beta_3$ quantify the effects of year, month, and category, respectively, while $\beta_4$ and $\beta_5$ capture the interaction effects.
+The error term $\epsilon_i$ accounts for the residual variability in crime counts not explained by the predictors, modeled with a Gaussian distribution.
+This setup allows the model to estimate the relative contributions of each predictor to crime counts and their combined effects on the observed trends.
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+## Model justification
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+The primary goal of this model is to forecast trends in vehicle-related crimes in Calgary, focusing on two categories: "Theft FROM Vehicle" and "Theft OF Vehicle." To achieve this, a Bayesian regression model was chosen, as it provides a robust framework for incorporating prior knowledge, handling uncertainty, and capturing complex relationships between predictors.
+
+The selection of predictors for the Bayesian regression model is grounded in their expected relationship with the response variable, crime_count, and their importance in explaining and forecasting trends in vehicle-related crimes.
+Below is a detailed justification for each predictor.
+
+### year(Numeric Predictor)
+
+The year variable is included as a numeric predictor because vehicle-related crimes are likely influenced by long-term trends over time.
+For instance, crime rates may decrease due to improvements in law enforcement strategies or community awareness campaigns.
+Conversely, they may increase due to economic downturns or population growth.
+By treating year as a continuous variable, the model can capture these gradual changes and make accurate predictions for future years, such as 2025.
+
+Relationship to Crime Counts: Crime counts for both categories ("Theft FROM Vehicle" and "Theft OF Vehicle") show clear temporal trends when plotted against year.
+For example, "Theft FROM Vehicle" demonstrates an overall decline in recent years, whereas "Theft OF Vehicle" shows a more gradual change (@fig-year-trend).
+
+```{r}
+#| label: fig-year-trend
+#| tbl-cap: Trend of Crime Counts Over Years
+#| echo: false
+#| warning: false
+
+ggplot(cleaned_data, aes(x = year, y = crime_count, color = category)) +
+  geom_point(alpha = 0.6) +
+  geom_smooth(method = "lm", se = FALSE) +
+  labs(
+    title = "Trend of Crime Counts Over Years",
+    x = "Year",
+    y = "Crime Count",
+    color = "Category"
+  ) +
+  theme_minimal()
+
+```
+
+### month (Categorical Predictor)
+
+The month variable is treated as a categorical predictor to account for seasonal variations in crime rates.
+Crime counts often fluctuate across months due to changes in weather, holidays, and other seasonal factors.
+For example, warmer months may see increased activity that could lead to more vehicle-related crimes, while colder months might see a decline.
+
+Relationship to Crime Counts: Monthly crime counts display seasonal patterns, with some months consistently showing higher crime rates than others.
+Including month as a categorical variable allows the model to account for these patterns without assuming a linear relationship.
+
+### category (Categorical Predictor)
+
+The category variable differentiates between "Theft FROM Vehicle" and "Theft OF Vehicle," two distinct types of crimes with different characteristics and frequencies.
+This variable is crucial for explaining the variation in crime counts, as the two categories exhibit different trends over time and across months.
+
+Relationship to Crime Counts: "Theft FROM Vehicle" has consistently higher crime counts than "Theft OF Vehicle." Additionally, the trends for these categories vary significantly over time and seasons, as seen in prior visualizations.
+By including category as a predictor, the model can capture these differences and provide more accurate predictions.
+
+### Interactions (Category:Month, Category:Year)
+
+Including interaction terms between category and time variables (month and year) allows the model to capture how the seasonal and yearly trends differ for "Theft FROM Vehicle" and "Theft OF Vehicle." For example, one category might experience sharper seasonal peaks or steeper declines over the years compared to the other.
+
+Relationship to Crime Counts: Visualizations of crime counts by year and month, separated by category, show evidence of these interactions.
+For instance, "Theft FROM Vehicle" exhibits more pronounced seasonal patterns and a sharper decline in recent years compared to "Theft OF Vehicle."
 
@@
 
-Our results are summarized in
+## Overview
+
+This study aims to address the research question: What is the forecasted trend for vehicle-related crimes in Calgary in 2025?
+Using a Bayesian regression model, we analyzed historical crime data from 2018 to 2024 and forecasted crime counts for 2025.
+The results are presented using summary statistics, regression estimates, and visualizations comparing actual and fitted trends.
+
+## Trends in Crime Counts
+
+The actual and fitted crime trends for both categories from 2018 to 2025 are shown in @fig-forcast-trend.
+The fitted values closely match the actual values, indicating the model's strong predictive accuracy.
 
 ```{r}
+#| label: fig-forcast-trend
+#| fig-cap: Actual vs. Fitted Crime Trends (2018-2025)
 #| echo: false
-#| eval: true
 #| warning: false
-#| message: false
+ggplot(fitted_data, aes(x = time, y = crime_count, color = category, linetype = source)) +
+  geom_line() +
+  labs(
+    title = "Actual vs. Fitted Crime Trends (2018-2025)",
+    x = "Time",
+    y = "Crime Count",
+    color = "Category",
+    linetype = "Source"
+  ) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+Theft FROM Vehicle: The crime counts show seasonal variability, with peaks during certain months (e.g., summer) and an overall declining trend.
+The model forecasts that this category will continue to decrease in 2025, with lower peak values and reduced seasonal fluctuations compared to earlier years.
+Theft OF Vehicle: This category exhibits a more consistent decline in crime counts over time, with fewer pronounced seasonal patterns.
+The model predicts further reductions in 2025, with crime counts stabilizing at relatively low levels.
+
+## Regression Model Estimates
+
+The regression model estimates, summarized in the @tbl-model-summary below, provide insight into how predictors such as year, month, and category influence vehicle-related crime counts in Calgary.
+The table includes coefficient estimates and their 95% confidence intervals to quantify the effect sizes and uncertainties associated with each predictor.
+
+```{r}
+#| label: tbl-model-summary
+#| tbl-cap: Regression Estimates for Crime Counts
+#| echo: false
+#| warning: false
+library(modelsummary)
+crime_model <- readRDS(here("models/crime_model.rds"))
+modelsummary(crime_model, 
+             statistic = c("conf.int"),
+             output = "markdown",
+             title = "Regression Estimates for Crime Counts")
 
@@
 
-```{r}
-#| echo: false
-#| eval: true
+### Year:
 
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
+The coefficient for Year is -60.4, indicating that on average, crime counts decrease by approximately 60 incidents per year for the reference category.
+This finding aligns with the observed overall decline in vehicle-related crime over time.
 
-```
+### Month:
+
+Monthly coefficients capture seasonal variations in crime counts relative to the reference month January.
+July and August exhibit higher-than-average crime counts, with estimates of 124.454 and 159.461, respectively, reflecting seasonal spikes during colder months.
+In contrast, December shows a lower-than-average count, with a negative estimate of -136.723, indicating fewer crimes during this period compared to January.
+
+### Category:
+
+The coefficient for Theft OF Vehicle is -437.470, showing that crime counts for "Theft OF Vehicle" are consistently lower than those for "Theft FROM Vehicle." This highlights the fundamental difference in frequency between the two categories.
+This finding reinforces the visual observation that "Theft FROM Vehicle" consistently exhibits higher counts than "Theft OF Vehicle."
+
+### Interaction Terms (Year × Category):
+
+The interaction term for Year and Theft OF Vehicle has an estimate of -0.011, suggesting that the declining trend in crime counts over time is slightly stronger for "Theft OF Vehicle" compared to "Theft FROM Vehicle."
+
+## Addressing the Research Question
+
+The model's results indicate that both types of vehicle-related crimes in Calgary are expected to decline in 2025. Key findings include:
+
+- Overall Decline: Both "Theft FROM Vehicle" and "Theft OF Vehicle" are forecasted to show lower crime counts compared to previous years.
+This decline reflects both long-term trends and recent reductions in crime rates.
+
+- Category Differences: "Theft FROM Vehicle" will remain more frequent than "Theft OF Vehicle," but the gap between the two categories is expected to narrow slightly as the decline in the former is more pronounced.
+
+- Seasonal Patterns: Seasonal fluctuations are expected to persist, especially for "Theft FROM Vehicle," but the peaks will be less pronounced than in earlier years.
+
+These findings suggest that crime prevention strategies targeting vehicle-related crimes have been effective and should continue to focus on mitigating seasonal spikes and addressing high-crime months.
+
+The Bayesian regression model provides strong evidence for declining trends in vehicle-related crimes in Calgary.
+By 2025, both categories are projected to experience reduced crime rates, with "Theft FROM Vehicle" showing a significant decrease in seasonal peaks and overall counts.
+These results offer valuable insights for law enforcement and policymakers, supporting the development of targeted strategies to maintain and accelerate these positive trends.
 
@@
 
-## First discussion point {#sec-first-point}
+## What Is Done in This Paper?
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+This paper investigates the trends and forecasts of vehicle-related crimes in Calgary, specifically focusing on the categories Theft FROM Vehicle and Theft OF Vehicle.
+Using historical data from 2018 to 2024 and a Bayesian regression model, the analysis identifies long-term trends, seasonal patterns, and differences between the two categories of crime.
+The model incorporates key predictors such as year, month, category, and their interactions to capture both temporal and categorical variations.
+The paper also provides forecasts for 2025, offering valuable insights into the expected future trends of these crimes.
 
-## Second discussion point
+## What Is Something That We Learn About the World?
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+One key finding from this study is the consistent decline in vehicle-related crimes over the years.
+The results suggest that crime prevention measures, technological advancements (such as better vehicle security systems), and targeted policing strategies may have contributed to this downward trend.
+The model also highlights seasonal patterns, particularly for Theft FROM Vehicle, which tends to peak in the summer months.
+These findings reinforce the idea that external factors such as weather, holiday travel, and increased outdoor activity can influence crime rates.
 
-## Third discussion point
+## What Is Another Thing That We Learn About the World?
 
-## Weaknesses and next steps
+Another important insight is the fundamental difference between the two crime categories.
+Theft FROM Vehicle is significantly more frequent than Theft OF Vehicle, and its seasonal variability is more pronounced.
+This suggests that theft from vehicles is opportunistic and influenced by environmental factors, whereas vehicle theft itself may be less seasonal and potentially driven by different motives, such as organized crime or professional theft rings.
+These differences imply that crime prevention strategies should be tailored to the specific characteristics of each category.
 
-Weaknesses and next steps should also be included.
+## Evaluating Policy Interventions
+
+A critical question arising from this research is how effective existing policy interventions have been in reducing vehicle-related crimes.
+While the model identifies a downward trend in both crime categories, it does not directly link these trends to specific policies, such as enhanced policing, public awareness campaigns, or technological improvements like vehicle immobilizers.
+Future research could assess the causal relationship between these interventions and crime reduction by incorporating data on policy implementation dates and intensity.
+For example, how did increased police patrols in high-crime areas or the introduction of anti-theft programs impact specific crime patterns?
+Addressing this question would provide a clearer understanding of which strategies work best and how they can be optimized.
+
+## What Are Some Weaknesses of What Was Done?
+
+While the analysis provides valuable insights, it is not without limitations:
+
+- Data Limitations: The study relies on historical data, which may not fully capture all relevant factors influencing crime trends.
+For example, socioeconomic conditions, population density, or enforcement policies are not explicitly included as predictors in the model.
+
+- Simplified Temporal Assumptions: The model assumes linear trends for year and constant seasonal effects for month.
+These assumptions may not capture potential nonlinearities or abrupt changes in crime patterns caused by external events (e.g., the COVID-19 pandemic or policy changes).
+
+- Interaction Complexity: Although the inclusion of interactions (e.g., Month × Category) improves the model, it may still oversimplify some complex relationships, particularly those involving latent or unobserved variables.
+
+- Forecasting Uncertainty: While the Bayesian framework quantifies uncertainty, the forecasts for 2025 remain dependent on the assumption that historical patterns will continue, which may not hold if new or unforeseen factors emerge.
 
@@
 
-# Appendix {-}
+# Model Diagnostics {#sec-model-detail}
 
-# Additional data details
+## Overview
 
-# Model details {#sec-model-details}
+To ensure the reliability and validity of the Bayesian regression model, a series of diagnostic checks were performed.
+These diagnostics evaluate the model's fit, the adequacy of the predictors, and whether the assumptions underlying the Bayesian framework are satisfied.
+Below is a detailed summary of the diagnostics conducted.
 
-## Posterior predictive check
+## Residual Analysis
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+Residuals @fig-residual-plot represent the differences between observed and predicted values and can indicate issues with model fit or violations of assumptions.
 
 ```{r}
-#| eval: true
+#| label: fig-residual-plot
+#| fig-cap: Residual Plot
 #| echo: false
-#| message: false
 #| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+
+# Residual plot
+residuals <- residuals(crime_model)
+plot(residuals, ylab = "Residuals", xlab = "Fitted Values", main = "Residual Plot")
+abline(h = 0, col = "red", lty = 2)
 
@@
 
-## Diagnostics
+The residual plot shows no discernible pattern, and residuals should be randomly scattered around zero.
+Patterns in the residuals (e.g., funnel shapes or trends) may indicate heteroscedasticity or omitted variable bias.
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+## Q-Q Plot
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+The Q-Q Plot @fig-qq assesses whether the residuals follow a normal distribution, which is an assumption of the Gaussian family used in the model.
+Deviations from the line in the Q-Q plot may suggest non-normality.
 
 ```{r}
+#| label: fig-qq
+#| fig-cap: Q-Q plots of Residuals
 #| echo: false
-#| eval: true
-#| message: false
 #| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
+#| 
+# Q-Q plot of residuals
+qqnorm(residuals, main = "Q-Q Plot of Residuals")
+qqline(residuals, col = "red", lty = 2)
 
 ```
+
+Residuals should fall approximately along the reference line.
+Significant deviations (e.g., at the tails) indicate potential violations of the normality assumption.
+For Bayesian models, slight deviations are tolerable.
+
+## Posterior Predictive Checks
+Posterior predictive checks were performed to evaluate how well the model's predictions align with the observed data.
+The density overlay plot @fig-posterior compares the observed crime counts to the posterior predictive distribution.
+
+```{r}
+#| label: fig-posterior
+#| fig-cap: Posterior Predictive Check
+#| echo: false
+#| warning: false
+
+pp_check(crime_model, plotfun = "dens_overlay") +
+  labs(title = "Posterior Predictive Check: Density Overlay")
+
+```
+
+The observed data aligns closely with the predictive distributions, indicating that the model captures the overall distribution of crime counts effectively.
+Any systematic mismatch could suggest model misspecification, but in this case, the results indicate good fit.
+
+# Idealized Methodology for Data Collection and Analysis{#sec-ideal-meth}
+
+## Overview
+
+This section explores an idealized methodology for improving the quality and comprehensiveness of data collection and analysis for vehicle-related crimes in Calgary.
+While the current study relies on observational data, an ideal approach would incorporate advanced survey methodologies, improved sampling techniques, and simulations to address limitations in the existing dataset.
+This methodological framework can enhance the reliability of findings and strengthen the connection between crime trends and causal factors.
+
+## Survey Design and Data Collection
+
+Comprehensive Crime Surveys:
+
+- Ideal Scenario: Conduct regular city-wide crime surveys that include questions about both reported and unreported vehicle-related crimes.
+
+- Purpose: Current data likely underreports actual crime counts due to reliance on police-reported incidents. Surveys can capture unreported cases, providing a fuller picture of crime trends.
+
+- Methodology: Use stratified random sampling to ensure representation from different neighborhoods, socioeconomic strata, and demographic groups.
+
+- Link to Literature: Surveys such as the British Crime Survey have demonstrated the value of incorporating unreported crimes into official statistics, highlighting disparities between reported and actual crime rates (Hough & Maxfield, 2007).
+
+Integration with Citizen-Generated Data:
+
+- Ideal Scenario: Incorporate data from mobile applications or online platforms where citizens can anonymously report crimes.
+
+- Purpose: Technology-driven reporting can supplement official data and improve coverage in areas with low reporting rates.
+
+- Implementation: Partner with local governments to develop secure, user-friendly platforms.
+
+## Sampling Methodology
+
+Randomized Geospatial Sampling:
+
+- Current Limitation: Observational data may over-represent areas with higher police presence or reporting infrastructure.
+
+- Ideal Scenario: Implement geospatial sampling techniques to collect crime data evenly across Calgary, ensuring inclusion of underrepresented areas.
+
+- Simulation Study: Simulate different sampling scenarios to evaluate their impact on data completeness and spatial bias reduction.
+
+Temporal Sampling:
+
+- Current Limitation: Monthly aggregation in the dataset may mask short-term spikes or declines in crime activity.
+
+- Ideal Scenario: Collect daily or weekly data to capture finer temporal variations in crime trends.
+
+- Example: A 2021 study on urban crime by Smith et al. showed that daily data improves the detection of time-sensitive factors like weather or public events.
 

### 2024-11-28 scripts/03-clean_data.R

@@ -23,5 +23,5 @@ cleaned_data <- raw_data %>% clean_names() %>%
 
 
 #### Save data ####
-write_csv(cleaned_data, "data/02-analysis_data/calgory_crime.csv")
-write_parquet(cleaned_data, "data/02-analysis_data/calgory_crime.parquet")
+write_csv(cleaned_data, "data/02-analysis_data/calgary_crime.csv")
+write_parquet(cleaned_data, "data/02-analysis_data/calgary_crime.parquet")

### 2024-11-28 scripts/05-model_data.R

@@ -13,7 +13,7 @@ library(ggplot2)
 library(dplyr)
 
 #### Read data ####
-crime_data <- read_parquet("data/02-analysis_data/calgory_crime.parquet")
+crime_data <- read_parquet("data/02-analysis_data/calgary_crime.parquet")
 
 ### Model data ####
 
@@ -78,4 +78,6 @@ saveRDS(
   file = "models/crime_model.rds"
 )
 
-
+#### Save Fitted Data ####
+write_csv(combined_data,"data/02-analysis_data/fitted_calgary_crime.csv")
+write_parquet(combined_data,"data/02-analysis_data/fitted_calgary_crime.parquet")

### 2024-11-28 paper/paper.tex
small change to the paper

--- 2024-11-28 paper/paper.qmd
@@
----
-title: "Focasting The Trend of Vehicle Related Crime In Calgary In 2025"
-subtitle: "An Analysis of Calgary's Crime Count From 2018 to 2024"
-author: 
-  - Haobo Ren
-thanks: "Code and data are available at: https://github.com/HaoboRrrr/calgary_vehicle_crime_forcast"
-date: 23-November-2024
-date-format: long
-abstract: "Vehicle-related crime is a long-standing challenge to urban security, so accurate prediction is necessary to effectively allocate police resources and develop security policies.
-This study examines trends in vehicle-related crime in Calgary, Canada, focusing on two types of crime: Theft of vehicle and Theft from vehicle.
-A Bayesian regression model is fit to historical crime data from January 2018 to October 2024, accounting for seasonal variations (months), long-term trends (years), and differences between crime categories.
-The usefulness of Bayesian modeling for crime trend forecasting is demonstrated by this analysis, providing law enforcement and policymakers practical insights to foresee and handle long-term and seasonal crime trends."
-format: pdf
-number-sections: true
-bibliography: references.bib
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
 
-```{r}
-#| include: false
-#| warning: false
-#| message: false
+\usepackage{amsmath,amssymb}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else  
+    % xetex/luatex font selection
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
+% Make \paragraph and \subparagraph free-standing
+\makeatletter
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+\makeatother
 
-library(tidyverse)
-library(here)
-library(knitr)
-library(arrow)
-library(ggplot2)
-library(bayesplot)
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
+  \fi
+  % set entry spacing
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-cleaned_data <- read_parquet(here("data/02-analysis_data/calgary_crime.parquet"))
-fitted_data <- read_parquet(here("data/02-analysis_data/fitted_calgary_crime.parquet"))
-```
+\usepackage{float}
+\usepackage{tabularray}
+\usepackage[normalem]{ulem}
+\usepackage{graphicx}
+\UseTblrLibrary{booktabs}
+\UseTblrLibrary{rotating}
+\UseTblrLibrary{siunitx}
+\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
+\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
+\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
+\KOMAoption{captions}{tableheading}
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
 
-# Introduction
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage{bookmark}
 
-Urban crime is an ongoing problem compromising public confidence, economic stability, and safety.
-Among the several types of crimes, vehicle-related offenses include theft of vehicles and theft from vehicles remain a major issue in urban areas across the country.
-These crimes disturb people's life but also burden local governments and law enforcement.
-Over the years, Calgary, Canada, has seen varying patterns in vehicle-related crimes, which raises issues regarding future developments of these trends.
-Designing effective preventive plans, maximizing resource allocation, and guaranteeing community safety all depend on an awareness of current trends and future crime count prediction.
-This study forecasts vehicle-related crime patterns in Calgary up until 2025, therefore addressing these issues.
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Focasting The Trend of Vehicle Related Crime In Calgary In 2025},
+  pdfauthor={Haobo Ren},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
-Analyzing and projecting monthly crime counts for theft from vehicles and theft of vehicles in Calgary is the main aim of this study.
-I created a Bayesian regression model to assess the effects of time (year and month) and crime category on reported crime counts using historical data spanning January 2018 through October 2024.
-Offering a comprehensive knowledge of how vehicle-related crimes have developed and may continue to alter in the near future, the model catches both long-term patterns and seasonal changes.
-The research also offers category-specific forecasts, therefore stressing variations in the seasonal and temporal trends of theft from and of vehicles.
+\title{Focasting The Trend of Vehicle Related Crime In Calgary In
+2025\thanks{Code and data are available at:
+https://github.com/HaoboRrrr/calgary\_vehicle\_crime\_forcast}}
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
+\subtitle{An Analysis of Calgary's Crime Count From 2018 to 2024}
+\author{Haobo Ren}
+\date{November 23, 2024}
 
-The analysis reveals a continued decline in vehicle-related crimes in Calgary, with a mean change of -60.4 each year, and notable mean differences of -435.0 between the two categories.
-Theft from vehicles is anticipated to show cyclical surges in the summer months, indicating possible opportunistic habits.
-Conversely, vehicle theft exhibits a more stable decline throughout the course of the year.
-The data indicate that, although overall vehicle-related crimes are down, seasonal surges in certain categories persist as a problem for policymakers and law enforcement to tackle, for example, the crime count of Theft From Vehicle in August is expected larger than January by 158.4.
+\begin{document}
+\maketitle
+\begin{abstract}
+Vehicle-related crime is a long-standing challenge to urban security, so
+accurate prediction is necessary to effectively allocate police
+resources and develop security policies. This study examines trends in
+vehicle-related crime in Calgary, Canada, focusing on two types of
+crime: Theft of vehicle and Theft from vehicle. A Bayesian regression
+model is fit to historical crime data from January 2018 to October 2024,
+accounting for seasonal variations (months), long-term trends (years),
+and differences between crime categories. The usefulness of Bayesian
+modeling for crime trend forecasting is demonstrated by this analysis,
+providing law enforcement and policymakers practical insights to foresee
+and handle long-term and seasonal crime trends.
+\end{abstract}
 
-The study is significant for its role in proactive crime prevention and resource optimization.
-This study offers precise and comprehensible forecasts, providing policymakers and law enforcement with evidence-based insights to inform decision-making.
-This study addresses a significant research gap and enhances public safety in Calgary.
+\section{Introduction}\label{introduction}
 
-#Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+Urban crime is an ongoing problem compromising public confidence,
+economic stability, and safety. Among the several types of crimes,
+vehicle-related offenses include theft of vehicles and theft from
+vehicles remain a major issue in urban areas across the country. These
+crimes disturb people's life but also burden local governments and law
+enforcement. Over the years, Calgary, Canada, has seen varying patterns
+in vehicle-related crimes, which raises issues regarding future
+developments of these trends. Designing effective preventive plans,
+maximizing resource allocation, and guaranteeing community safety all
+depend on an awareness of current trends and future crime count
+prediction. This study forecasts vehicle-related crime patterns in
+Calgary up until 2025, therefore addressing these issues.
 
-# Data {#sec-data}
+Analyzing and projecting monthly crime counts for theft from vehicles
+and theft of vehicles in Calgary is the main aim of this study. I
+created a Bayesian regression model to assess the effects of time (year
+and month) and crime category on reported crime counts using historical
+data spanning January 2018 through October 2024. Offering a
+comprehensive knowledge of how vehicle-related crimes have developed and
+may continue to alter in the near future, the model catches both
+long-term patterns and seasonal changes. The research also offers
+category-specific forecasts, therefore stressing variations in the
+seasonal and temporal trends of theft from and of vehicles.
 
-## Overview
+The analysis reveals a continued decline in vehicle-related crimes in
+Calgary, with a mean change of -60.4 each year, and notable mean
+differences of -435.0 between the two categories. Theft from vehicles is
+anticipated to show cyclical surges in the summer months, indicating
+possible opportunistic habits. Conversely, vehicle theft exhibits a more
+stable decline throughout the course of the year. The data indicate
+that, although overall vehicle-related crimes are down, seasonal surges
+in certain categories persist as a problem for policymakers and law
+enforcement to tackle, for example, the crime count of Theft From
+Vehicle in August is expected larger than January by 158.4.
 
-The raw dataset obtained from Open Data Calgary[@OpenCalgary] was recorded and updated monthly by the Calgary Police Service.
-The data is considered cumulative as late-reported incidents are often received well after an offence has occurred.
-An incident is either reported just after the crime happened, or reported on the Calgary Police Service[@calgarypolice].
+The study is significant for its role in proactive crime prevention and
+resource optimization. This study offers precise and comprehensible
+forecasts, providing policymakers and law enforcement with
+evidence-based insights to inform decision-making. This study addresses
+a significant research gap and enhances public safety in Calgary.
 
-The data analysis and visualization is done in R[@citeR] with the following Packages: tidyverse[@tidy], janitor[@janitor], arrow[@arrow], rstanarm[@rstanarm], ggplot2[@ggplot2], dplyr[@dplyr], here, knitr.
+\#Telegraphing paragraph: The remainder of this paper is structured as
+follows. Section~\ref{sec-data}\ldots.
 
-## Measurement
+\section{Data}\label{sec-data}
 
-The data reflects reported crime incidents across Calgary, categorized by community, crime type, and temporal details (year and month).
-Each row in the dataset represents a summary of crime counts for a specific category and community within a given month and year.
-The Calgary Police Service serves as the primary source, systematically recording incidents reported by the public.
-These reports may be filed in several ways, including: immediate Reporting and delayed Reporting.
+\subsection{Overview}\label{overview}
 
-Crime count quantifies the number of reported incidents of a specific crime and time period and is based on the most serious violation per incident.
-The count represents and aggregation of individual reports collected by the Calgary Police Services.
+The raw dataset obtained from Open Data Calgary(Calgary, n.d.) was
+recorded and updated monthly by the Calgary Police Service. The data is
+considered cumulative as late-reported incidents are often received well
+after an offence has occurred. An incident is either reported just after
+the crime happened, or reported on the Calgary Police Service(Service,
+n.d.).
 
-There are limitations in these measurement.
-Reporting Bias: Not all crimes are reported.
-Minor incidents or those involving uninsured vehicles may go unreported, leading to underestimation of true crime rates.
-Cumulative Nature: The inclusion of late-reported incidents makes it challenging to distinguish between crimes that occurred during the reported month versus those that occurred earlier.
+The data analysis and visualization is done in R(R Core Team 2023) with
+the following Packages: tidyverse(Wickham et al. 2019), janitor(Firke
+2023), arrow(Richardson et al. 2024), rstanarm(Goodrich et al. 2022),
+ggplot2(Wickham 2016), dplyr(Wickham et al. 2022), here, knitr.
 
-By understanding how this dataset measures real-world crime phenomena, we can more confidently interpret the insights and predictions derived from it.
+\subsection{Measurement}\label{measurement}
 
-## Data Examination {#sec-dataexam}
+The data reflects reported crime incidents across Calgary, categorized
+by community, crime type, and temporal details (year and month). Each
+row in the dataset represents a summary of crime counts for a specific
+category and community within a given month and year. The Calgary Police
+Service serves as the primary source, systematically recording incidents
+reported by the public. These reports may be filed in several ways,
+including: immediate Reporting and delayed Reporting.
 
-The raw data from Open Data has five columns and 75,595 rows, the column names are displayed below:
+Crime count quantifies the number of reported incidents of a specific
+crime and time period and is based on the most serious violation per
+incident. The count represents and aggregation of individual reports
+collected by the Calgary Police Services.
 
-```{r}
-#| echo: false
-#| warning: false
-raw_data <- read_csv(here("data/01-raw_data/raw_data.csv"))
+There are limitations in these measurement. Reporting Bias: Not all
+crimes are reported. Minor incidents or those involving uninsured
+vehicles may go unreported, leading to underestimation of true crime
+rates. Cumulative Nature: The inclusion of late-reported incidents makes
+it challenging to distinguish between crimes that occurred during the
+reported month versus those that occurred earlier.
 
-# Get the column names of your raw data
-column_names <- colnames(raw_data)
+By understanding how this dataset measures real-world crime phenomena,
+we can more confidently interpret the insights and predictions derived
+from it.
 
-# Convert the column names to a data frame for kable
-column_df <- as.data.frame(column_names)
+\subsection{Data Examination}\label{sec-dataexam}
 
-# Display with kable
-kable(column_df)
-```
-- Community: The dataset is spatially disaggregated into Calgary's various communities
+The raw data from Open Data has five columns and 75,595 rows, the column
+names are displayed below:
+
+\begin{longtable}[]{@{}l@{}}
+\toprule\noalign{}
+column\_names \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Community \\
+Category \\
+Crime Count \\
+Year \\
+Month \\
+\end{longtable}
+
+\begin{itemize}
+\tightlist
+\item
+  Community: The dataset is spatially disaggregated into Calgary's
+  various communities
+\end{itemize}
 
@@
 
-- Year: The year of each record indicate when the incidents were reported.
+\begin{itemize}
+\tightlist
+\item
+  Year: The year of each record indicate when the incidents were
+  reported.
+\end{itemize}
 
@@
 
-- Category: Each entry is categorized into distinct crime types.
-
-- month: The month of each incidents recorded. Range from 1-12 repeatedly each year
+\begin{itemize}
+\item
+  Category: Each entry is categorized into distinct crime types.
+\item
+  month: The month of each incidents recorded. Range from 1-12
+  repeatedly each year
+\end{itemize}
 
@@
 
-- Crime Count: This variable quantifies the number of reported incidents of a specific crime type (e.g., theft from or of vehicles) within a given community and time period.
+\begin{itemize}
+\tightlist
+\item
+  Crime Count: This variable quantifies the number of reported incidents
+  of a specific crime type (e.g., theft from or of vehicles) within a
+  given community and time period.
+\end{itemize}
 
-## Data Cleaning
+\subsection{Data Cleaning}\label{data-cleaning}
 
-Several steps was taken for better analysis of vehicle-related trend in Calgary.
-First, clean the names of all the columns.
-Second, the raw dataset contained granular records categorized by Community and specific details.
-These were aggregated to provide summarized counts of crimes (crime_count) by category, year, and month to align with analysis requirements.
-Third, a new time column was introduced in the cleaned data, combining year and month into a single date field (YYYY-MM-DD).
-This was essential for time-series analysis and visualization.
-Last, filter out the categories related to vehicle.
+Several steps was taken for better analysis of vehicle-related trend in
+Calgary. First, clean the names of all the columns. Second, the raw
+dataset contained granular records categorized by Community and specific
+details. These were aggregated to provide summarized counts of crimes
+(crime\_count) by category, year, and month to align with analysis
+requirements. Third, a new time column was introduced in the cleaned
+data, combining year and month into a single date field (YYYY-MM-DD).
+This was essential for time-series analysis and visualization. Last,
+filter out the categories related to vehicle.
 
-## Cleaned Data
+\subsection{Cleaned Data}\label{cleaned-data}
 
-The first 6 rows of the cleaned dataset are shown in @tbl-cleaned-data.
+The first 6 rows of the cleaned dataset are shown in
+Table~\ref{tbl-cleaned-data}.
 
-```{r}
-#| label: tbl-cleaned-data
-#| tbl-cap: Head of cleaned Calgary Crime data 
-#| echo: false
-#| warning: false
+\begin{longtable}[]{@{}lrrrl@{}}
 
-kable(head(cleaned_data))
-```
+\caption{\label{tbl-cleaned-data}Head of cleaned Calgary Crime data}
 
-## Response Variable
+\tabularnewline
 
-### Crime count of Theft FROM Vehicle
+\toprule\noalign{}
+category & crime\_count & year & month & time \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Theft FROM Vehicle & 962 & 2018 & 1 & 2018-01-01 \\
+Theft FROM Vehicle & 645 & 2018 & 2 & 2018-02-01 \\
+Theft FROM Vehicle & 818 & 2018 & 3 & 2018-03-01 \\
+Theft FROM Vehicle & 870 & 2018 & 4 & 2018-04-01 \\
+Theft FROM Vehicle & 1063 & 2018 & 5 & 2018-05-01 \\
+Theft FROM Vehicle & 1036 & 2018 & 6 & 2018-06-01 \\
 
-Summary statistics of Crime count of Theft FROM Vehicle are shown in the @tbl-response-theftfromvehicle
+\end{longtable}
 
-```{r}
-#| label: tbl-response-theftfromvehicle
-#| tbl-cap: Summary Statitic of crime_count(Theft FROM Vehicle)
-#| echo: false
-#| warning: false
+\subsection{Response Variable}\label{response-variable}
 
-kable(cleaned_data %>% filter(category == "Theft FROM Vehicle") %>% select(crime_count) %>% summary(crime_count))
-```
+\subsubsection{Crime count of Theft FROM
+Vehicle}\label{crime-count-of-theft-from-vehicle}
 
-The response variable, crime_count, represents the number of reported incidents of theft from vehicles within Calgary.
-The summary statistics reveal a significant variability in the crime counts, ranging from a minimum of 120 to a maximum of 1,619 reported cases.
-The median value is 916, indicating that half of the recorded months experienced fewer than 916 thefts, while the other half exceeded this value.
-The mean crime count, at 932.7, is slightly higher than the median, suggesting the presence of months with particularly high crime counts that may be skewing the average.
-The interquartile range (IQR), spanning from 788.2 (1st quartile) to 1,105.5 (3rd quartile), highlights the central tendency of crime occurrences, with most months falling within this range.
-These statistics emphasize the fluctuating nature of vehicle thefts in Calgary and provide a foundational understanding for modeling and forecasting future trends.
+Summary statistics of Crime count of Theft FROM Vehicle are shown in the
+Table~\ref{tbl-response-theftfromvehicle}
 
-### Crime count of Theft OF Vehicle
+\begin{longtable}[]{@{}ll@{}}
 
-Summary statistics of Crime count of Theft FROM Vehicle are shown in the @tbl-response-theftofvehicle
+\caption{\label{tbl-response-theftfromvehicle}Summary Statitic of
+crime\_count(Theft FROM Vehicle)}
 
-```{r}
-#| label: tbl-response-theftofvehicle
-#| tbl-cap: Summary Statitic of crime_count(Theft OF Vehicle)
-#| echo: false
-#| warning: false
+\tabularnewline
 
-kable(cleaned_data %>% filter(category == "Theft OF Vehicle") %>% select(crime_count) %>% summary(crime_count))
-```
+\toprule\noalign{}
+& crime\_count \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+& Min. : 120.0 \\
+& 1st Qu.: 788.2 \\
+& Median : 916.0 \\
+& Mean : 932.7 \\
+& 3rd Qu.:1105.5 \\
+& Max. :1619.0 \\
 
-The response variable, crime_count, for Theft OF Vehicle incidents reflects the monthly reported counts of vehicles being stolen in Calgary.
-The dataset's summary statistics indicate that the crime counts range from a minimum of 146 to a maximum of 651 incidents.
-The median count is 424.5, suggesting that half of the months have fewer than 425 thefts, while the other half exceed this value.
-Interestingly, the mean crime count is 422.5, closely aligned with the median, suggesting a relatively symmetric distribution of the data.
-The interquartile range (IQR) spans from 361.2 (1st quartile) to 469.0 (3rd quartile), indicating that most monthly counts are concentrated within this range.
-These figures highlight the scale and regularity of vehicle theft in Calgary and form an essential basis for analyzing and forecasting trends in such crimes.
+\end{longtable}
 
-## Predictor Variable
+The response variable, crime\_count, represents the number of reported
+incidents of theft from vehicles within Calgary. The summary statistics
+reveal a significant variability in the crime counts, ranging from a
+minimum of 120 to a maximum of 1,619 reported cases. The median value is
+916, indicating that half of the recorded months experienced fewer than
+916 thefts, while the other half exceeded this value. The mean crime
+count, at 932.7, is slightly higher than the median, suggesting the
+presence of months with particularly high crime counts that may be
+skewing the average. The interquartile range (IQR), spanning from 788.2
+(1st quartile) to 1,105.5 (3rd quartile), highlights the central
+tendency of crime occurrences, with most months falling within this
+range. These statistics emphasize the fluctuating nature of vehicle
+thefts in Calgary and provide a foundational understanding for modeling
+and forecasting future trends.
 
-### year
+\subsubsection{Crime count of Theft OF
+Vehicle}\label{crime-count-of-theft-of-vehicle}
 
-The variable year represents the timeline over which the crime data is recorded, providing insight into how vehicle-related crime counts have changed annually.
-By analyzing the data across different years, we can observe any long-term trends, such as consistent increases, decreases, or fluctuations in vehicle thefts.
-This variable helps us understand whether certain years experienced higher crime rates due to factors like economic conditions, population changes, or other external influences.
+Summary statistics of Crime count of Theft FROM Vehicle are shown in the
+Table~\ref{tbl-response-theftofvehicle}
 
-### month and category
+\begin{longtable}[]{@{}ll@{}}
 
-The variables month and category provide a detailed view of how vehicle-related crimes are distributed across time and crime types.
-Month captures seasonal variations, showing how crime rates fluctuate throughout the year.
-For example, there might be a tendency for higher crime counts during certain seasons, such as summer or winter, influenced by weather conditions or holiday activities.
-Category distinguishes between "Theft FROM Vehicle" and "Theft OF Vehicle," allowing us to compare the frequency and patterns of these two crime types.
-Together, these variables highlight differences in the nature and timing of vehicle-related crimes, offering valuable insights into their temporal and categorical distributions.
+\caption{\label{tbl-response-theftofvehicle}Summary Statitic of
+crime\_count(Theft OF Vehicle)}
 
-## Trend of The Two Crime
+\tabularnewline
 
-The trend of Theft FROM Vehicle and Theft OF Vehicle are shown in @fig-combined-trend
+\toprule\noalign{}
+& crime\_count \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+& Min. :146.0 \\
+& 1st Qu.:361.2 \\
+& Median :424.5 \\
+& Mean :422.5 \\
+& 3rd Qu.:469.0 \\
+& Max. :651.0 \\
 
-```{r}
-#| label: fig-combined-trend
-#| fig-cap: Trend of The Two Crime Combined
-#| echo: false
-#| warning: false
-# Plot combined trends
-ggplot(cleaned_data, aes(x = time, y = crime_count, color = category)) +
-  geom_line() +
-  labs(
-    title = "Trend of Theft FROM Vehicle and Theft OF Vehicle",
-    x = "Time",
-    y = "Crime Count",
-    color = "Category"
-  ) +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
+\end{longtable}
+
+The response variable, crime\_count, for Theft OF Vehicle incidents
+reflects the monthly reported counts of vehicles being stolen in
+Calgary. The dataset's summary statistics indicate that the crime counts
+range from a minimum of 146 to a maximum of 651 incidents. The median
+count is 424.5, suggesting that half of the months have fewer than 425
+thefts, while the other half exceed this value. Interestingly, the mean
+crime count is 422.5, closely aligned with the median, suggesting a
+relatively symmetric distribution of the data. The interquartile range
+(IQR) spans from 361.2 (1st quartile) to 469.0 (3rd quartile),
+indicating that most monthly counts are concentrated within this range.
+These figures highlight the scale and regularity of vehicle theft in
+Calgary and form an essential basis for analyzing and forecasting trends
+in such crimes.
+
+\subsection{Predictor Variable}\label{predictor-variable}
+
+\subsubsection{year}\label{year}
+
+The variable year represents the timeline over which the crime data is
+recorded, providing insight into how vehicle-related crime counts have
+changed annually. By analyzing the data across different years, we can
+observe any long-term trends, such as consistent increases, decreases,
+or fluctuations in vehicle thefts. This variable helps us understand
+whether certain years experienced higher crime rates due to factors like
+economic conditions, population changes, or other external influences.
+
+\subsubsection{month and category}\label{month-and-category}
+
+The variables month and category provide a detailed view of how
+vehicle-related crimes are distributed across time and crime types.
+Month captures seasonal variations, showing how crime rates fluctuate
+throughout the year. For example, there might be a tendency for higher
+crime counts during certain seasons, such as summer or winter,
+influenced by weather conditions or holiday activities. Category
+distinguishes between ``Theft FROM Vehicle'' and ``Theft OF Vehicle,''
+allowing us to compare the frequency and patterns of these two crime
+types. Together, these variables highlight differences in the nature and
+timing of vehicle-related crimes, offering valuable insights into their
+temporal and categorical distributions.
+
+\subsection{Trend of The Two Crime}\label{trend-of-the-two-crime}
+
+The trend of Theft FROM Vehicle and Theft OF Vehicle are shown in
+Figure~\ref{fig-combined-trend}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-combined-trend-1.pdf}
+
+}
+
+\caption{\label{fig-combined-trend}Trend of The Two Crime Combined}
+
+\end{figure}%
+
 \newpage
 
-The trends for "Theft FROM Vehicle" and "Theft OF Vehicle" reveal distinct patterns over time.
-"Theft FROM Vehicle" consistently shows higher crime counts compared to "Theft OF Vehicle," indicating that it is a more prevalent issue.
-The trend for "Theft FROM Vehicle" demonstrates significant fluctuations, with peaks around 2019 and a general decline afterward, suggesting a reduction in these incidents in more recent years.
-In contrast, "Theft OF Vehicle" exhibits a relatively stable pattern with smaller variations over time.
-Although it remains less frequent than "Theft FROM Vehicle," its counts appear to decrease gradually, particularly after 2022.
-Both categories show declining trends toward the end of the observed period, which could reflect successful crime prevention measures or other external influences.
+The trends for ``Theft FROM Vehicle'' and ``Theft OF Vehicle'' reveal
+distinct patterns over time. ``Theft FROM Vehicle'' consistently shows
+higher crime counts compared to ``Theft OF Vehicle,'' indicating that it
+is a more prevalent issue. The trend for ``Theft FROM Vehicle''
+demonstrates significant fluctuations, with peaks around 2019 and a
+general decline afterward, suggesting a reduction in these incidents in
+more recent years. In contrast, ``Theft OF Vehicle'' exhibits a
+relatively stable pattern with smaller variations over time. Although it
+remains less frequent than ``Theft FROM Vehicle,'' its counts appear to
+decrease gradually, particularly after 2022. Both categories show
+declining trends toward the end of the observed period, which could
+reflect successful crime prevention measures or other external
+influences.
 
-# Model
+\section{Model}\label{model}
 
-The Bayesian regression model was developed to analyze and forecast the trends of vehicle-related crimes in Calgary, focusing on the categories "Theft FROM Vehicle" and "Theft OF Vehicle." The primary goal of this modeling is to understand the relationship between crime counts and key predictors such as time (year and month) and crime categories, as well as their interactions.
-By incorporating temporal and categorical variables, the model seeks to capture long-term trends, seasonal patterns, and differences between the two types of crimes.
-Ultimately, the model provides a foundation for projecting future crime rates, offering valuable insights that can support strategic decision-making and the development of targeted crime prevention initiatives for 2025 and beyond.
+The Bayesian regression model was developed to analyze and forecast the
+trends of vehicle-related crimes in Calgary, focusing on the categories
+``Theft FROM Vehicle'' and ``Theft OF Vehicle.'' The primary goal of
+this modeling is to understand the relationship between crime counts and
+key predictors such as time (year and month) and crime categories, as
+well as their interactions. By incorporating temporal and categorical
+variables, the model seeks to capture long-term trends, seasonal
+patterns, and differences between the two types of crimes. Ultimately,
+the model provides a foundation for projecting future crime rates,
+offering valuable insights that can support strategic decision-making
+and the development of targeted crime prevention initiatives for 2025
+and beyond.
 
-Background details and diagnostics are included in [Appendix -@sec-model-details].
+Background details and diagnostics are included in
+\textbf{?@sec-model-details}.
 
-## Model set-up
+\subsection{Model set-up}\label{model-set-up}
 
-The Bayesian regression model is set up to examine the relationship between vehicle-related crime counts and the selected predictors.
-The response variable, $y_i$, represents the observed crime count for the i-th observation, where each observation corresponds to a specific month, year, and crime category.
-The predictors include a numeric variable for year, categorical variables for month and category, as well as interaction terms (category:month and category:year) to capture how crime patterns differ between the two crime types over time and across seasons.
+The Bayesian regression model is set up to examine the relationship
+between vehicle-related crime counts and the selected predictors. The
+response variable, \(y_i\), represents the observed crime count for the
+i-th observation, where each observation corresponds to a specific
+month, year, and crime category. The predictors include a numeric
+variable for year, categorical variables for month and category, as well
+as interaction terms (category:month and category:year) to capture how
+crime patterns differ between the two crime types over time and across
+seasons.
 
@@
 
-$$
+\[
 y_i = \beta_0 + \beta_1 \text{year}_i + \beta_2 \text{month}_i + \beta_3 \text{category}_i + \beta_4 (\text{category} \times \text{month})_i + \beta_5 (\text{category} \times \text{year})_i + \epsilon_i
-$$
+\]
 
-Here, $\beta_0$ is the intercept, capturing the baseline level of crime counts.
-The coefficients $\beta_1$, $\beta_2$, and $\beta_3$ quantify the effects of year, month, and category, respectively, while $\beta_4$ and $\beta_5$ capture the interaction effects.
-The error term $\epsilon_i$ accounts for the residual variability in crime counts not explained by the predictors, modeled with a Gaussian distribution.
-This setup allows the model to estimate the relative contributions of each predictor to crime counts and their combined effects on the observed trends.
+Here, \(\beta_0\) is the intercept, capturing the baseline level of
+crime counts. The coefficients \(\beta_1\), \(\beta_2\), and \(\beta_3\)
+quantify the effects of year, month, and category, respectively, while
+\(\beta_4\) and \(\beta_5\) capture the interaction effects. The error
+term \(\epsilon_i\) accounts for the residual variability in crime
+counts not explained by the predictors, modeled with a Gaussian
+distribution. This setup allows the model to estimate the relative
+contributions of each predictor to crime counts and their combined
+effects on the observed trends.
 
-## Model justification
+\subsection{Model justification}\label{model-justification}
 
-The primary goal of this model is to forecast trends in vehicle-related crimes in Calgary, focusing on two categories: "Theft FROM Vehicle" and "Theft OF Vehicle." To achieve this, a Bayesian regression model was chosen, as it provides a robust framework for incorporating prior knowledge, handling uncertainty, and capturing complex relationships between predictors.
+The primary goal of this model is to forecast trends in vehicle-related
+crimes in Calgary, focusing on two categories: ``Theft FROM Vehicle''
+and ``Theft OF Vehicle.'' To achieve this, a Bayesian regression model
+was chosen, as it provides a robust framework for incorporating prior
+knowledge, handling uncertainty, and capturing complex relationships
+between predictors.
 
-The selection of predictors for the Bayesian regression model is grounded in their expected relationship with the response variable, crime_count, and their importance in explaining and forecasting trends in vehicle-related crimes.
-Below is a detailed justification for each predictor.
+The selection of predictors for the Bayesian regression model is
+grounded in their expected relationship with the response variable,
+crime\_count, and their importance in explaining and forecasting trends
+in vehicle-related crimes. Below is a detailed justification for each
+predictor.
 
-### year(Numeric Predictor)
+\subsubsection{year(Numeric Predictor)}\label{yearnumeric-predictor}
 
-The year variable is included as a numeric predictor because vehicle-related crimes are likely influenced by long-term trends over time.
-For instance, crime rates may decrease due to improvements in law enforcement strategies or community awareness campaigns.
-Conversely, they may increase due to economic downturns or population growth.
-By treating year as a continuous variable, the model can capture these gradual changes and make accurate predictions for future years, such as 2025.
+The year variable is included as a numeric predictor because
+vehicle-related crimes are likely influenced by long-term trends over
+time. For instance, crime rates may decrease due to improvements in law
+enforcement strategies or community awareness campaigns. Conversely,
+they may increase due to economic downturns or population growth. By
+treating year as a continuous variable, the model can capture these
+gradual changes and make accurate predictions for future years, such as
+2025.
 
-Relationship to Crime Counts: Crime counts for both categories ("Theft FROM Vehicle" and "Theft OF Vehicle") show clear temporal trends when plotted against year.
-For example, "Theft FROM Vehicle" demonstrates an overall decline in recent years, whereas "Theft OF Vehicle" shows a more gradual change (@fig-year-trend).
+Relationship to Crime Counts: Crime counts for both categories (``Theft
+FROM Vehicle'' and ``Theft OF Vehicle'') show clear temporal trends when
+plotted against year. For example, ``Theft FROM Vehicle'' demonstrates
+an overall decline in recent years, whereas ``Theft OF Vehicle'' shows a
+more gradual change (Figure~\ref{fig-year-trend}).
 
-```{r}
-#| label: fig-year-trend
-#| tbl-cap: Trend of Crime Counts Over Years
-#| echo: false
-#| warning: false
+\begin{figure}
 
-ggplot(cleaned_data, aes(x = year, y = crime_count, color = category)) +
-  geom_point(alpha = 0.6) +
-  geom_smooth(method = "lm", se = FALSE) +
-  labs(
-    title = "Trend of Crime Counts Over Years",
-    x = "Year",
-    y = "Crime Count",
-    color = "Category"
-  ) +
-  theme_minimal()
+\centering{
 
-```
+\includegraphics{paper_files/figure-pdf/fig-year-trend-1.pdf}
 
-### month (Categorical Predictor)
+}
 
-The month variable is treated as a categorical predictor to account for seasonal variations in crime rates.
-Crime counts often fluctuate across months due to changes in weather, holidays, and other seasonal factors.
-For example, warmer months may see increased activity that could lead to more vehicle-related crimes, while colder months might see a decline.
+\caption{\label{fig-year-trend}}
 
-Relationship to Crime Counts: Monthly crime counts display seasonal patterns, with some months consistently showing higher crime rates than others.
-Including month as a categorical variable allows the model to account for these patterns without assuming a linear relationship.
+\end{figure}%
 
-### category (Categorical Predictor)
+\subsubsection{month (Categorical
+Predictor)}\label{month-categorical-predictor}
 
-The category variable differentiates between "Theft FROM Vehicle" and "Theft OF Vehicle," two distinct types of crimes with different characteristics and frequencies.
-This variable is crucial for explaining the variation in crime counts, as the two categories exhibit different trends over time and across months.
+The month variable is treated as a categorical predictor to account for
+seasonal variations in crime rates. Crime counts often fluctuate across
+months due to changes in weather, holidays, and other seasonal factors.
+For example, warmer months may see increased activity that could lead to
+more vehicle-related crimes, while colder months might see a decline.
 
-Relationship to Crime Counts: "Theft FROM Vehicle" has consistently higher crime counts than "Theft OF Vehicle." Additionally, the trends for these categories vary significantly over time and seasons, as seen in prior visualizations.
-By including category as a predictor, the model can capture these differences and provide more accurate predictions.
+Relationship to Crime Counts: Monthly crime counts display seasonal
+patterns, with some months consistently showing higher crime rates than
+others. Including month as a categorical variable allows the model to
+account for these patterns without assuming a linear relationship.
 
-### Interactions (Category:Month, Category:Year)
+\subsubsection{category (Categorical
+Predictor)}\label{category-categorical-predictor}
 
-Including interaction terms between category and time variables (month and year) allows the model to capture how the seasonal and yearly trends differ for "Theft FROM Vehicle" and "Theft OF Vehicle." For example, one category might experience sharper seasonal peaks or steeper declines over the years compared to the other.
+The category variable differentiates between ``Theft FROM Vehicle'' and
+``Theft OF Vehicle,'' two distinct types of crimes with different
+characteristics and frequencies. This variable is crucial for explaining
+the variation in crime counts, as the two categories exhibit different
+trends over time and across months.
 
-Relationship to Crime Counts: Visualizations of crime counts by year and month, separated by category, show evidence of these interactions.
-For instance, "Theft FROM Vehicle" exhibits more pronounced seasonal patterns and a sharper decline in recent years compared to "Theft OF Vehicle."
+Relationship to Crime Counts: ``Theft FROM Vehicle'' has consistently
+higher crime counts than ``Theft OF Vehicle.'' Additionally, the trends
+for these categories vary significantly over time and seasons, as seen
+in prior visualizations. By including category as a predictor, the model
+can capture these differences and provide more accurate predictions.
 
-# Results
+\subsubsection{Interactions (Category:Month,
+Category:Year)}\label{interactions-categorymonth-categoryyear}
 
-## Overview
+Including interaction terms between category and time variables (month
+and year) allows the model to capture how the seasonal and yearly trends
+differ for ``Theft FROM Vehicle'' and ``Theft OF Vehicle.'' For example,
+one category might experience sharper seasonal peaks or steeper declines
+over the years compared to the other.
 
-This study aims to address the research question: What is the forecasted trend for vehicle-related crimes in Calgary in 2025?
-Using a Bayesian regression model, we analyzed historical crime data from 2018 to 2024 and forecasted crime counts for 2025.
-The results are presented using summary statistics, regression estimates, and visualizations comparing actual and fitted trends.
+Relationship to Crime Counts: Visualizations of crime counts by year and
+month, separated by category, show evidence of these interactions. For
+instance, ``Theft FROM Vehicle'' exhibits more pronounced seasonal
+patterns and a sharper decline in recent years compared to ``Theft OF
+Vehicle.''
 
-## Trends in Crime Counts
+\section{Results}\label{results}
 
-The actual and fitted crime trends for both categories from 2018 to 2025 are shown in @fig-forcast-trend.
-The fitted values closely match the actual values, indicating the model's strong predictive accuracy.
+\subsection{Overview}\label{overview-1}
 
-```{r}
-#| label: fig-forcast-trend
-#| fig-cap: Actual vs. Fitted Crime Trends (2018-2025)
-#| echo: false
-#| warning: false
-ggplot(fitted_data, aes(x = time, y = crime_count, color = category, linetype = source)) +
-  geom_line() +
-  labs(
-    title = "Actual vs. Fitted Crime Trends (2018-2025)",
-    x = "Time",
-    y = "Crime Count",
-    color = "Category",
-    linetype = "Source"
-  ) +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
+This study aims to address the research question: What is the forecasted
+trend for vehicle-related crimes in Calgary in 2025? Using a Bayesian
+regression model, we analyzed historical crime data from 2018 to 2024
+and forecasted crime counts for 2025. The results are presented using
+summary statistics, regression estimates, and visualizations comparing
+actual and fitted trends.
 
-Theft FROM Vehicle: The crime counts show seasonal variability, with peaks during certain months (e.g., summer) and an overall declining trend.
-The model forecasts that this category will continue to decrease in 2025, with lower peak values and reduced seasonal fluctuations compared to earlier years.
-Theft OF Vehicle: This category exhibits a more consistent decline in crime counts over time, with fewer pronounced seasonal patterns.
-The model predicts further reductions in 2025, with crime counts stabilizing at relatively low levels.
+\subsection{Trends in Crime Counts}\label{trends-in-crime-counts}
 
-## Regression Model Estimates
+The actual and fitted crime trends for both categories from 2018 to 2025
+are shown in Figure~\ref{fig-forcast-trend}. The fitted values closely
+match the actual values, indicating the model's strong predictive
+accuracy.
 
-The regression model estimates, summarized in the @tbl-model-summary below, provide insight into how predictors such as year, month, and category influence vehicle-related crime counts in Calgary.
-The table includes coefficient estimates and their 95% confidence intervals to quantify the effect sizes and uncertainties associated with each predictor.
+\begin{figure}
 
-```{r}
-#| label: tbl-model-summary
-#| tbl-cap: Regression Estimates for Crime Counts
-#| echo: false
-#| warning: false
-library(modelsummary)
-crime_model <- readRDS(here("models/crime_model.rds"))
-modelsummary(crime_model, 
-             statistic = c("conf.int"),
-             output = "markdown",
-             title = "Regression Estimates for Crime Counts")
+\centering{
 
-```
+\includegraphics{paper_files/figure-pdf/fig-forcast-trend-1.pdf}
 
-### Year:
+}
 
-The coefficient for Year is -60.4, indicating that on average, crime counts decrease by approximately 60 incidents per year for the reference category.
-This finding aligns with the observed overall decline in vehicle-related crime over time.
+\caption{\label{fig-forcast-trend}Actual vs.~Fitted Crime Trends
+(2018-2025)}
 
-### Month:
+\end{figure}%
 
-Monthly coefficients capture seasonal variations in crime counts relative to the reference month January.
-July and August exhibit higher-than-average crime counts, with estimates of 124.454 and 159.461, respectively, reflecting seasonal spikes during colder months.
-In contrast, December shows a lower-than-average count, with a negative estimate of -136.723, indicating fewer crimes during this period compared to January.
+Theft FROM Vehicle: The crime counts show seasonal variability, with
+peaks during certain months (e.g., summer) and an overall declining
+trend. The model forecasts that this category will continue to decrease
+in 2025, with lower peak values and reduced seasonal fluctuations
+compared to earlier years. Theft OF Vehicle: This category exhibits a
+more consistent decline in crime counts over time, with fewer pronounced
+seasonal patterns. The model predicts further reductions in 2025, with
+crime counts stabilizing at relatively low levels.
 
-### Category:
+\subsection{Regression Model
+Estimates}\label{regression-model-estimates}
 
-The coefficient for Theft OF Vehicle is -437.470, showing that crime counts for "Theft OF Vehicle" are consistently lower than those for "Theft FROM Vehicle." This highlights the fundamental difference in frequency between the two categories.
-This finding reinforces the visual observation that "Theft FROM Vehicle" consistently exhibits higher counts than "Theft OF Vehicle."
+The regression model estimates, summarized in the
+Table~\ref{tbl-model-summary} below, provide insight into how predictors
+such as year, month, and category influence vehicle-related crime counts
+in Calgary. The table includes coefficient estimates and their 95\%
+confidence intervals to quantify the effect sizes and uncertainties
+associated with each predictor.
 
-### Interaction Terms (Year × Category):
+\begin{table}
 
-The interaction term for Year and Theft OF Vehicle has an estimate of -0.011, suggesting that the declining trend in crime counts over time is slightly stronger for "Theft OF Vehicle" compared to "Theft FROM Vehicle."
+\caption{\label{tbl-model-summary}Regression Estimates for Crime Counts}
 
-## Addressing the Research Question
+\centering{
 
-The model's results indicate that both types of vehicle-related crimes in Calgary are expected to decline in 2025. Key findings include:
+\centering
+\begin{talltblr}[         %% tabularray outer open
+caption={Regression Estimates for Crime Counts},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]},
+column{1}={halign=l,},
+column{2}={halign=c,},
+hline{54}={1,2}{solid, 0.05em, black},
+}                     %% tabularray inner close
+\toprule
+& (1) \\ \midrule %% TinyTableHeader
+(Intercept)                        & 123057.381              \\
+& [96510.352, 150616.116] \\
+year                               & -60.433                 \\
+& [-74.054, -47.276]      \\
+month2                             & -164.798                \\
+& [-347.666, 18.539]      \\
+month3                             & -42.071                 \\
+& [-222.917, 142.358]     \\
+month4                             & -23.889                 \\
+& [-194.463, 150.747]     \\
+month5                             & 16.104                  \\
+& [-163.861, 195.906]     \\
+month6                             & 31.509                  \\
+& [-152.950, 207.755]     \\
+month7                             & 124.454                 \\
+& [-52.165, 303.685]      \\
+month8                             & 159.461                 \\
+& [-13.010, 335.016]      \\
+month9                             & 97.048                  \\
+& [-82.968, 273.083]      \\
+month10                            & -3.361                  \\
+& [-187.237, 178.705]     \\
+month11                            & -24.549                 \\
+& [-205.024, 168.499]     \\
+month12                            & -136.723                \\
+& [-324.726, 48.464]      \\
+categoryTheft OF Vehicle           & -437.570                \\
+& [-2742.242, 1801.269]   \\
+month2 × categoryTheft OF Vehicle  & 122.011                 \\
+& [-134.730, 378.015]     \\
+month3 × categoryTheft OF Vehicle  & 9.826                   \\
+& [-246.309, 259.061]     \\
+month4 × categoryTheft OF Vehicle  & -36.909                 \\
+& [-292.718, 204.047]     \\
+month5 × categoryTheft OF Vehicle  & -107.952                \\
+& [-353.079, 155.633]     \\
+month6 × categoryTheft OF Vehicle  & -121.642                \\
+& [-375.451, 137.567]     \\
+month7 × categoryTheft OF Vehicle  & -134.351                \\
+& [-389.202, 108.424]     \\
+month8 × categoryTheft OF Vehicle  & -187.926                \\
+& [-436.928, 58.410]      \\
+month9 × categoryTheft OF Vehicle  & -134.800                \\
+& [-385.293, 123.208]     \\
+month10 × categoryTheft OF Vehicle & -76.343                 \\
+& [-341.169, 171.960]     \\
+month11 × categoryTheft OF Vehicle & -65.365                 \\
+& [-328.735, 202.691]     \\
+month12 × categoryTheft OF Vehicle & 69.075                  \\
+& [-195.011, 336.640]     \\
+year × categoryTheft OF Vehicle    & -0.011                  \\
+& [-1.117, 1.132]         \\
+Num.Obs.                           & 164                     \\
+R2                                 & 0.752                   \\
+R2 Adj.                            & 0.693                   \\
+Log.Lik.                           & -1065.045               \\
+ELPD                               & -1089.5                 \\
+ELPD s.e.                          & 11.6                    \\
+LOOIC                              & 2178.9                  \\
+LOOIC s.e.                         & 23.2                    \\
+WAIC                               & 2177.8                  \\
+RMSE                               & 156.23                  \\
+\bottomrule
+\end{talltblr}
 
-- Overall Decline: Both "Theft FROM Vehicle" and "Theft OF Vehicle" are forecasted to show lower crime counts compared to previous years.
-This decline reflects both long-term trends and recent reductions in crime rates.
+}
 
-- Category Differences: "Theft FROM Vehicle" will remain more frequent than "Theft OF Vehicle," but the gap between the two categories is expected to narrow slightly as the decline in the former is more pronounced.
+\end{table}%
 
-- Seasonal Patterns: Seasonal fluctuations are expected to persist, especially for "Theft FROM Vehicle," but the peaks will be less pronounced than in earlier years.
+\subsubsection{Year:}\label{year-1}
 
-These findings suggest that crime prevention strategies targeting vehicle-related crimes have been effective and should continue to focus on mitigating seasonal spikes and addressing high-crime months.
+The coefficient for Year is -60.4, indicating that on average, crime
+counts decrease by approximately 60 incidents per year for the reference
+category. This finding aligns with the observed overall decline in
+vehicle-related crime over time.
 
-The Bayesian regression model provides strong evidence for declining trends in vehicle-related crimes in Calgary.
-By 2025, both categories are projected to experience reduced crime rates, with "Theft FROM Vehicle" showing a significant decrease in seasonal peaks and overall counts.
-These results offer valuable insights for law enforcement and policymakers, supporting the development of targeted strategies to maintain and accelerate these positive trends.
+\subsubsection{Month:}\label{month}
 
-# Discussion
+Monthly coefficients capture seasonal variations in crime counts
+relative to the reference month January. July and August exhibit
+higher-than-average crime counts, with estimates of 124.454 and 159.461,
+respectively, reflecting seasonal spikes during colder months. In
+contrast, December shows a lower-than-average count, with a negative
+estimate of -136.723, indicating fewer crimes during this period
+compared to January.
 
-## What Is Done in This Paper?
+\subsubsection{Category:}\label{category}
 
-This paper investigates the trends and forecasts of vehicle-related crimes in Calgary, specifically focusing on the categories Theft FROM Vehicle and Theft OF Vehicle.
-Using historical data from 2018 to 2024 and a Bayesian regression model, the analysis identifies long-term trends, seasonal patterns, and differences between the two categories of crime.
-The model incorporates key predictors such as year, month, category, and their interactions to capture both temporal and categorical variations.
-The paper also provides forecasts for 2025, offering valuable insights into the expected future trends of these crimes.
+The coefficient for Theft OF Vehicle is -437.470, showing that crime
+counts for ``Theft OF Vehicle'' are consistently lower than those for
+``Theft FROM Vehicle.'' This highlights the fundamental difference in
+frequency between the two categories. This finding reinforces the visual
+observation that ``Theft FROM Vehicle'' consistently exhibits higher
+counts than ``Theft OF Vehicle.''
 
-## What Is Something That We Learn About the World?
+\subsubsection{Interaction Terms (Year ×
+Category):}\label{interaction-terms-year-category}
 
-One key finding from this study is the consistent decline in vehicle-related crimes over the years.
-The results suggest that crime prevention measures, technological advancements (such as better vehicle security systems), and targeted policing strategies may have contributed to this downward trend.
-The model also highlights seasonal patterns, particularly for Theft FROM Vehicle, which tends to peak in the summer months.
-These findings reinforce the idea that external factors such as weather, holiday travel, and increased outdoor activity can influence crime rates.
+The interaction term for Year and Theft OF Vehicle has an estimate of
+-0.011, suggesting that the declining trend in crime counts over time is
+slightly stronger for ``Theft OF Vehicle'' compared to ``Theft FROM
+Vehicle.''
 
-## What Is Another Thing That We Learn About the World?
+\subsection{Addressing the Research
+Question}\label{addressing-the-research-question}
 
-Another important insight is the fundamental difference between the two crime categories.
-Theft FROM Vehicle is significantly more frequent than Theft OF Vehicle, and its seasonal variability is more pronounced.
-This suggests that theft from vehicles is opportunistic and influenced by environmental factors, whereas vehicle theft itself may be less seasonal and potentially driven by different motives, such as organized crime or professional theft rings.
-These differences imply that crime prevention strategies should be tailored to the specific characteristics of each category.
+The model's results indicate that both types of vehicle-related crimes
+in Calgary are expected to decline in 2025. Key findings include:
 
-## Evaluating Policy Interventions
+\begin{itemize}
+\item
+  Overall Decline: Both ``Theft FROM Vehicle'' and ``Theft OF Vehicle''
+  are forecasted to show lower crime counts compared to previous years.
+  This decline reflects both long-term trends and recent reductions in
+  crime rates.
+\item
+  Category Differences: ``Theft FROM Vehicle'' will remain more frequent
+  than ``Theft OF Vehicle,'' but the gap between the two categories is
+  expected to narrow slightly as the decline in the former is more
+  pronounced.
+\item
+  Seasonal Patterns: Seasonal fluctuations are expected to persist,
+  especially for ``Theft FROM Vehicle,'' but the peaks will be less
+  pronounced than in earlier years.
+\end{itemize}
 
-A critical question arising from this research is how effective existing policy interventions have been in reducing vehicle-related crimes.
-While the model identifies a downward trend in both crime categories, it does not directly link these trends to specific policies, such as enhanced policing, public awareness campaigns, or technological improvements like vehicle immobilizers.
-Future research could assess the causal relationship between these interventions and crime reduction by incorporating data on policy implementation dates and intensity.
-For example, how did increased police patrols in high-crime areas or the introduction of anti-theft programs impact specific crime patterns?
-Addressing this question would provide a clearer understanding of which strategies work best and how they can be optimized.
+These findings suggest that crime prevention strategies targeting
+vehicle-related crimes have been effective and should continue to focus
+on mitigating seasonal spikes and addressing high-crime months.
 
-## What Are Some Weaknesses of What Was Done?
+The Bayesian regression model provides strong evidence for declining
+trends in vehicle-related crimes in Calgary. By 2025, both categories
+are projected to experience reduced crime rates, with ``Theft FROM
+Vehicle'' showing a significant decrease in seasonal peaks and overall
+counts. These results offer valuable insights for law enforcement and
+policymakers, supporting the development of targeted strategies to
+maintain and accelerate these positive trends.
 
-While the analysis provides valuable insights, it is not without limitations:
+\section{Discussion}\label{discussion}
 
-- Data Limitations: The study relies on historical data, which may not fully capture all relevant factors influencing crime trends.
-For example, socioeconomic conditions, population density, or enforcement policies are not explicitly included as predictors in the model.
+\subsection{What Is Done in This
+Paper?}\label{what-is-done-in-this-paper}
 
-- Simplified Temporal Assumptions: The model assumes linear trends for year and constant seasonal effects for month.
-These assumptions may not capture potential nonlinearities or abrupt changes in crime patterns caused by external events (e.g., the COVID-19 pandemic or policy changes).
+This paper investigates the trends and forecasts of vehicle-related
+crimes in Calgary, specifically focusing on the categories Theft FROM
+Vehicle and Theft OF Vehicle. Using historical data from 2018 to 2024
+and a Bayesian regression model, the analysis identifies long-term
+trends, seasonal patterns, and differences between the two categories of
+crime. The model incorporates key predictors such as year, month,
+category, and their interactions to capture both temporal and
+categorical variations. The paper also provides forecasts for 2025,
+offering valuable insights into the expected future trends of these
+crimes.
 
-- Interaction Complexity: Although the inclusion of interactions (e.g., Month × Category) improves the model, it may still oversimplify some complex relationships, particularly those involving latent or unobserved variables.
+\subsection{What Is Something That We Learn About the
+World?}\label{what-is-something-that-we-learn-about-the-world}
 
-- Forecasting Uncertainty: While the Bayesian framework quantifies uncertainty, the forecasts for 2025 remain dependent on the assumption that historical patterns will continue, which may not hold if new or unforeseen factors emerge.
+One key finding from this study is the consistent decline in
+vehicle-related crimes over the years. The results suggest that crime
+prevention measures, technological advancements (such as better vehicle
+security systems), and targeted policing strategies may have contributed
+to this downward trend. The model also highlights seasonal patterns,
+particularly for Theft FROM Vehicle, which tends to peak in the summer
+months. These findings reinforce the idea that external factors such as
+weather, holiday travel, and increased outdoor activity can influence
+crime rates.
+
+\subsection{What Is Another Thing That We Learn About the
+World?}\label{what-is-another-thing-that-we-learn-about-the-world}
+
+Another important insight is the fundamental difference between the two
+crime categories. Theft FROM Vehicle is significantly more frequent than
+Theft OF Vehicle, and its seasonal variability is more pronounced. This
+suggests that theft from vehicles is opportunistic and influenced by
+environmental factors, whereas vehicle theft itself may be less seasonal
+and potentially driven by different motives, such as organized crime or
+professional theft rings. These differences imply that crime prevention
+strategies should be tailored to the specific characteristics of each
+category.
+
+\subsection{Evaluating Policy
+Interventions}\label{evaluating-policy-interventions}
+
+A critical question arising from this research is how effective existing
+policy interventions have been in reducing vehicle-related crimes. While
+the model identifies a downward trend in both crime categories, it does
+not directly link these trends to specific policies, such as enhanced
+policing, public awareness campaigns, or technological improvements like
+vehicle immobilizers. Future research could assess the causal
+relationship between these interventions and crime reduction by
+incorporating data on policy implementation dates and intensity. For
+example, how did increased police patrols in high-crime areas or the
+introduction of anti-theft programs impact specific crime patterns?
+Addressing this question would provide a clearer understanding of which
+strategies work best and how they can be optimized.
+
+\subsection{What Are Some Weaknesses of What Was
+Done?}\label{what-are-some-weaknesses-of-what-was-done}
+
+While the analysis provides valuable insights, it is not without
+limitations:
+
+\begin{itemize}
+\item
+  Data Limitations: The study relies on historical data, which may not
+  fully capture all relevant factors influencing crime trends. For
+  example, socioeconomic conditions, population density, or enforcement
+  policies are not explicitly included as predictors in the model.
+\item
+  Simplified Temporal Assumptions: The model assumes linear trends for
+  year and constant seasonal effects for month. These assumptions may
+  not capture potential nonlinearities or abrupt changes in crime
+  patterns caused by external events (e.g., the COVID-19 pandemic or
+  policy changes).
+\item
+  Interaction Complexity: Although the inclusion of interactions (e.g.,
+  Month × Category) improves the model, it may still oversimplify some
+  complex relationships, particularly those involving latent or
+  unobserved variables.
+\item
+  Forecasting Uncertainty: While the Bayesian framework quantifies
+  uncertainty, the forecasts for 2025 remain dependent on the assumption
+  that historical patterns will continue, which may not hold if new or
+  unforeseen factors emerge.
+\end{itemize}
 
@@
 
-# Model Diagnostics {#sec-model-detail}
+\section{Model Diagnostics}\label{sec-model-detail}
 
-## Overview
+\subsection{Overview}\label{overview-2}
 
-To ensure the reliability and validity of the Bayesian regression model, a series of diagnostic checks were performed.
-These diagnostics evaluate the model's fit, the adequacy of the predictors, and whether the assumptions underlying the Bayesian framework are satisfied.
-Below is a detailed summary of the diagnostics conducted.
+To ensure the reliability and validity of the Bayesian regression model,
+a series of diagnostic checks were performed. These diagnostics evaluate
+the model's fit, the adequacy of the predictors, and whether the
+assumptions underlying the Bayesian framework are satisfied. Below is a
+detailed summary of the diagnostics conducted.
 
-## Residual Analysis
+\subsection{Residual Analysis}\label{residual-analysis}
 
-Residuals @fig-residual-plot represent the differences between observed and predicted values and can indicate issues with model fit or violations of assumptions.
+Residuals Figure~\ref{fig-residual-plot} represent the differences
+between observed and predicted values and can indicate issues with model
+fit or violations of assumptions.
 
-```{r}
-#| label: fig-residual-plot
-#| fig-cap: Residual Plot
-#| echo: false
-#| warning: false
+\begin{figure}
 
-# Residual plot
-residuals <- residuals(crime_model)
-plot(residuals, ylab = "Residuals", xlab = "Fitted Values", main = "Residual Plot")
-abline(h = 0, col = "red", lty = 2)
+\centering{
 
-```
+\includegraphics{paper_files/figure-pdf/fig-residual-plot-1.pdf}
 
-The residual plot shows no discernible pattern, and residuals should be randomly scattered around zero.
-Patterns in the residuals (e.g., funnel shapes or trends) may indicate heteroscedasticity or omitted variable bias.
+}
 
-## Q-Q Plot
+\caption{\label{fig-residual-plot}Residual Plot}
 
-The Q-Q Plot @fig-qq assesses whether the residuals follow a normal distribution, which is an assumption of the Gaussian family used in the model.
-Deviations from the line in the Q-Q plot may suggest non-normality.
+\end{figure}%
 
-```{r}
-#| label: fig-qq
-#| fig-cap: Q-Q plots of Residuals
-#| echo: false
-#| warning: false
-#| 
-# Q-Q plot of residuals
-qqnorm(residuals, main = "Q-Q Plot of Residuals")
-qqline(residuals, col = "red", lty = 2)
+The residual plot shows no discernible pattern, and residuals should be
+randomly scattered around zero. Patterns in the residuals (e.g., funnel
+shapes or trends) may indicate heteroscedasticity or omitted variable
+bias.
 
-```
+\subsection{Q-Q Plot}\label{q-q-plot}
+
+The Q-Q Plot Figure~\ref{fig-qq} assesses whether the residuals follow a
+normal distribution, which is an assumption of the Gaussian family used
+in the model. Deviations from the line in the Q-Q plot may suggest
+non-normality.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-qq-1.pdf}
+
+}
+
+\caption{\label{fig-qq}Q-Q plots of Residuals}
+
+\end{figure}%
 
 Residuals should fall approximately along the reference line.
-Significant deviations (e.g., at the tails) indicate potential violations of the normality assumption.
-For Bayesian models, slight deviations are tolerable.
+Significant deviations (e.g., at the tails) indicate potential
+violations of the normality assumption. For Bayesian models, slight
+deviations are tolerable.
 
-## Posterior Predictive Checks
-Posterior predictive checks were performed to evaluate how well the model's predictions align with the observed data.
-The density overlay plot @fig-posterior compares the observed crime counts to the posterior predictive distribution.
+\subsection{Posterior Predictive
+Checks}\label{posterior-predictive-checks}
 
-```{r}
-#| label: fig-posterior
-#| fig-cap: Posterior Predictive Check
-#| echo: false
-#| warning: false
+Posterior predictive checks were performed to evaluate how well the
+model's predictions align with the observed data. The density overlay
+plot Figure~\ref{fig-posterior} compares the observed crime counts to
+the posterior predictive distribution.
 
-pp_check(crime_model, plotfun = "dens_overlay") +
-  labs(title = "Posterior Predictive Check: Density Overlay")
+\begin{figure}
 
-```
+\centering{
 
-The observed data aligns closely with the predictive distributions, indicating that the model captures the overall distribution of crime counts effectively.
-Any systematic mismatch could suggest model misspecification, but in this case, the results indicate good fit.
+\includegraphics{paper_files/figure-pdf/fig-posterior-1.pdf}
 
-# Idealized Methodology for Data Collection and Analysis{#sec-ideal-meth}
+}
 
-## Overview
+\caption{\label{fig-posterior}Posterior Predictive Check}
 
-This section explores an idealized methodology for improving the quality and comprehensiveness of data collection and analysis for vehicle-related crimes in Calgary.
-While the current study relies on observational data, an ideal approach would incorporate advanced survey methodologies, improved sampling techniques, and simulations to address limitations in the existing dataset.
-This methodological framework can enhance the reliability of findings and strengthen the connection between crime trends and causal factors.
+\end{figure}%
 
-## Survey Design and Data Collection
+The observed data aligns closely with the predictive distributions,
+indicating that the model captures the overall distribution of crime
+counts effectively. Any systematic mismatch could suggest model
+misspecification, but in this case, the results indicate good fit.
+
+\section{Idealized Methodology for Data Collection and
+Analysis}\label{sec-ideal-meth}
+
+\subsection{Overview}\label{overview-3}
+
+This section explores an idealized methodology for improving the quality
+and comprehensiveness of data collection and analysis for
+vehicle-related crimes in Calgary. While the current study relies on
+observational data, an ideal approach would incorporate advanced survey
+methodologies, improved sampling techniques, and simulations to address
+limitations in the existing dataset. This methodological framework can
+enhance the reliability of findings and strengthen the connection
+between crime trends and causal factors.
+
+\subsection{Survey Design and Data
+Collection}\label{survey-design-and-data-collection}
 
@@
 
-- Ideal Scenario: Conduct regular city-wide crime surveys that include questions about both reported and unreported vehicle-related crimes.
-
-- Purpose: Current data likely underreports actual crime counts due to reliance on police-reported incidents. Surveys can capture unreported cases, providing a fuller picture of crime trends.
-
-- Methodology: Use stratified random sampling to ensure representation from different neighborhoods, socioeconomic strata, and demographic groups.
-
-- Link to Literature: Surveys such as the British Crime Survey have demonstrated the value of incorporating unreported crimes into official statistics, highlighting disparities between reported and actual crime rates (Hough & Maxfield, 2007).
+\begin{itemize}
+\item
+  Ideal Scenario: Conduct regular city-wide crime surveys that include
+  questions about both reported and unreported vehicle-related crimes.
+\item
+  Purpose: Current data likely underreports actual crime counts due to
+  reliance on police-reported incidents. Surveys can capture unreported
+  cases, providing a fuller picture of crime trends.
+\item
+  Methodology: Use stratified random sampling to ensure representation
+  from different neighborhoods, socioeconomic strata, and demographic
+  groups.
+\item
+  Link to Literature: Surveys such as the British Crime Survey have
+  demonstrated the value of incorporating unreported crimes into
+  official statistics, highlighting disparities between reported and
+  actual crime rates (Hough \& Maxfield, 2007).
+\end{itemize}
 
@@
 
-- Ideal Scenario: Incorporate data from mobile applications or online platforms where citizens can anonymously report crimes.
+\begin{itemize}
+\item
+  Ideal Scenario: Incorporate data from mobile applications or online
+  platforms where citizens can anonymously report crimes.
+\item
+  Purpose: Technology-driven reporting can supplement official data and
+  improve coverage in areas with low reporting rates.
+\item
+  Implementation: Partner with local governments to develop secure,
+  user-friendly platforms.
+\end{itemize}
 
-- Purpose: Technology-driven reporting can supplement official data and improve coverage in areas with low reporting rates.
-
-- Implementation: Partner with local governments to develop secure, user-friendly platforms.
-
-## Sampling Methodology
+\subsection{Sampling Methodology}\label{sampling-methodology}
 
@@
 
-- Current Limitation: Observational data may over-represent areas with higher police presence or reporting infrastructure.
-
-- Ideal Scenario: Implement geospatial sampling techniques to collect crime data evenly across Calgary, ensuring inclusion of underrepresented areas.
-
-- Simulation Study: Simulate different sampling scenarios to evaluate their impact on data completeness and spatial bias reduction.
+\begin{itemize}
+\item
+  Current Limitation: Observational data may over-represent areas with
+  higher police presence or reporting infrastructure.
+\item
+  Ideal Scenario: Implement geospatial sampling techniques to collect
+  crime data evenly across Calgary, ensuring inclusion of
+  underrepresented areas.
+\item
+  Simulation Study: Simulate different sampling scenarios to evaluate
+  their impact on data completeness and spatial bias reduction.
+\end{itemize}
 
@@
 
-- Current Limitation: Monthly aggregation in the dataset may mask short-term spikes or declines in crime activity.
-
-- Ideal Scenario: Collect daily or weekly data to capture finer temporal variations in crime trends.
-
-- Example: A 2021 study on urban crime by Smith et al. showed that daily data improves the detection of time-sensitive factors like weather or public events.
+\begin{itemize}
+\item
+  Current Limitation: Monthly aggregation in the dataset may mask
+  short-term spikes or declines in crime activity.
+\item
+  Ideal Scenario: Collect daily or weekly data to capture finer temporal
+  variations in crime trends.
+\item
+  Example: A 2021 study on urban crime by Smith et al.~showed that daily
+  data improves the detection of time-sensitive factors like weather or
+  public events.
+\end{itemize}
 
@@
 
-# References
+\section*{References}\label{references}
+\addcontentsline{toc}{section}{References}
+
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-OpenCalgary}
+Calgary, Open. n.d. \emph{Open Calgary}. \url{https://data.calgary.ca/}.
+
+\bibitem[\citeproctext]{ref-janitor}
+Firke, Sam. 2023. \emph{Janitor: Simple Tools for Examining and Cleaning
+Dirty Data}. \url{https://CRAN.R-project.org/package=janitor}.
+
+\bibitem[\citeproctext]{ref-rstanarm}
+Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
+{``{rstanarm: {Bayesian} applied regression modeling via {Stan}}.''}
+\url{https://mc-stan.org/rstanarm/}.
+
+\bibitem[\citeproctext]{ref-citeR}
+R Core Team. 2023. \emph{{R: A Language and Environment for Statistical
+Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}.
+
+\bibitem[\citeproctext]{ref-arrow}
+Richardson, Neal, Ian Cook, Nic Crane, Dewey Dunnington, Romain
+François, Jonathan Keane, Dragoș Moldovan-Grünfeld, Jeroen Ooms, Jacob
+Wujciak-Jens, and Apache Arrow. 2024. \emph{Arrow: Integration to
+'Apache' 'Arrow'}. \url{https://CRAN.R-project.org/package=arrow}.
+
+\bibitem[\citeproctext]{ref-calgarypolice}
+Service, Calgary Police. n.d. \emph{The City of Calgary - Home Page}.
+\url{https://www.calgary.ca/cps.html}.
+
+\bibitem[\citeproctext]{ref-ggplot2}
+Wickham, Hadley. 2016. \emph{Ggplot2: Elegant Graphics for Data
+Analysis}. Springer-Verlag New York.
+\url{https://ggplot2.tidyverse.org}.
+
+\bibitem[\citeproctext]{ref-tidy}
+Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
+D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
+{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
+4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.
+
+\bibitem[\citeproctext]{ref-dplyr}
+Wickham, Hadley, Romain François, Lionel Henry, and Kirill Müller. 2022.
+\emph{Dplyr: A Grammar of Data Manipulation}.
+
+\end{CSLReferences}
+
+\end{document}

### 2024-11-29 paper/paper.qmd
Edit paper and fix cross reference

@@
 
-Urban crime is an ongoing problem compromising public confidence, economic stability, and safety.
-Among the several types of crimes, vehicle-related offenses include theft of vehicles and theft from vehicles remain a major issue in urban areas across the country.
+Urban crime is an ongoing problem compromising public confidence, economic stability, and safety[@un2012enhancing].
+Among the several types of crimes, vehicle-related offenses include theft of vehicles and theft from vehicles remain a major issue in urban areas across the country[@rakauskas2009identification].
 These crimes disturb people's life but also burden local governments and law enforcement.
@@
 
-The analysis reveals a continued decline in vehicle-related crimes in Calgary, with a mean change of -60.4 each year, and notable mean differences of -435.0 between the two categories.
+The analysis reveals a continued decline in vehicle-related crimes in Calgary, with a mean change of -60.5 each year, and notable mean differences of -454.8 between the two categories.
 Theft from vehicles is anticipated to show cyclical surges in the summer months, indicating possible opportunistic habits.
 Conversely, vehicle theft exhibits a more stable decline throughout the course of the year.
-The data indicate that, although overall vehicle-related crimes are down, seasonal surges in certain categories persist as a problem for policymakers and law enforcement to tackle, for example, the crime count of Theft From Vehicle in August is expected larger than January by 158.4.
+The data indicate that, although overall vehicle-related crimes are down, seasonal surges in certain categories persist as a problem for policymakers and law enforcement to tackle, for example, the crime count of Theft From Vehicle in August is expected larger than January by 159.4.
+Details are in @sec-result.
 
@@
 
-#Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+The remainder of this paper is structured as follows: @sec-data provides an overview of the data.
+@sec-model provides the modeling approach.
+@sec-result present the results and discuss the implications, limitations.
+@sec-discussion.
 
@@
 
-The data analysis and visualization is done in R[@citeR] with the following Packages: tidyverse[@tidy], janitor[@janitor], arrow[@arrow], rstanarm[@rstanarm], ggplot2[@ggplot2], dplyr[@dplyr], here, knitr.
+The data analysis and visualization is done in R[@citeR] with the following Packages: tidyverse[@tidy], janitor[@janitor], arrow[@arrow], rstanarm[@rstanarm], ggplot2[@ggplot2], dplyr[@dplyr], here[@here], knitr[@knitr], and bayesplot[@bayes].
 
@@
 
-The raw data from Open Data has five columns and 75,595 rows, the column names are displayed below:
+The raw data from Open Data has five columns and 75,595 rows, the column names are displayed below: @tbl-raw
 
 ```{r}
+#| label: tbl-raw
+#| tbl-cap: Column Names of Raw Data
 #| echo: false
@@
 
-# Model
+# Model {#sec-model}
 
@@
 
-Background details and diagnostics are included in [Appendix -@sec-model-details].
+Background details and diagnostics are included in Appendix @sec-model-detail.
 
@@
 Below is a detailed justification for each predictor.
+More detailed justification and test of model are in @sec-model-detail
 
@@
 
-# Results
+# Results {#sec-result}
 
@@
 The regression model estimates, summarized in the @tbl-model-summary below, provide insight into how predictors such as year, month, and category influence vehicle-related crime counts in Calgary.
-The table includes coefficient estimates and their 95% confidence intervals to quantify the effect sizes and uncertainties associated with each predictor.
+The table includes coefficient estimates and their standard deviation to quantify the effect sizes and uncertainties associated with each predictor.
 
@@
 crime_model <- readRDS(here("models/crime_model.rds"))
-modelsummary(crime_model, 
-             statistic = c("conf.int"),
-             output = "markdown",
-             title = "Regression Estimates for Crime Counts")
+
+# Extract the model summary as a matrix
+model_summary <- summary(crime_model)
+
+# Convert the summary into a data frame
+summary_table <- as.data.frame(model_summary)
+
+# Rename the columns for clarity
+colnames(summary_table) <- c("Mean", "SD", "10%", "50%", "90%")
+
+# Round the "Mean" and "SD" columns to 2 decimal places
+summary_table$Mean <- round(summary_table$Mean, 1)
+summary_table$SD <- round(summary_table$SD, 1)
+
+kable(summary_table %>% select("Mean", "SD"))
 
@@
 
-The coefficient for Year is -60.4, indicating that on average, crime counts decrease by approximately 60 incidents per year for the reference category.
+The coefficient for Year is -60.5, indicating that on average, crime counts decrease by approximately 60 incidents per year for the reference category.
 This finding aligns with the observed overall decline in vehicle-related crime over time.
@@
 Monthly coefficients capture seasonal variations in crime counts relative to the reference month January.
-July and August exhibit higher-than-average crime counts, with estimates of 124.454 and 159.461, respectively, reflecting seasonal spikes during colder months.
-In contrast, December shows a lower-than-average count, with a negative estimate of -136.723, indicating fewer crimes during this period compared to January.
+July and August exhibit higher-than-average crime counts, with estimates of 123.8 and 159.4, respectively, reflecting seasonal spikes during colder months.
+In contrast, December shows a lower-than-average count, with a negative estimate of -134.8, indicating fewer crimes during this period compared to January.
 
@@
 
-The coefficient for Theft OF Vehicle is -437.470, showing that crime counts for "Theft OF Vehicle" are consistently lower than those for "Theft FROM Vehicle." This highlights the fundamental difference in frequency between the two categories.
+The coefficient for Theft OF Vehicle is -454.8, showing that crime counts for "Theft OF Vehicle" are consistently lower than those for "Theft FROM Vehicle." This highlights the fundamental difference in frequency between the two categories.
 This finding reinforces the visual observation that "Theft FROM Vehicle" consistently exhibits higher counts than "Theft OF Vehicle."
@@
 
-The interaction term for Year and Theft OF Vehicle has an estimate of -0.011, suggesting that the declining trend in crime counts over time is slightly stronger for "Theft OF Vehicle" compared to "Theft FROM Vehicle."
+The interaction term for Year and Theft OF Vehicle has an estimate of 0.0, suggesting that the declining trend in crime counts over time is statistically no difference between "Theft OF Vehicle" and "Theft FROM Vehicle."
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 

### 2024-11-29 scripts/05-model_data.R

@@ -16,7 +16,7 @@ library(dplyr)
 crime_data <- read_parquet("data/02-analysis_data/calgary_crime.parquet")
 
 ### Model data ####
-
+set.seed(123)
 # Ensure `category` is treated as a factor
 crime_data$category <- as.factor(crime_data$category)
 crime_data$month <- as.factor(crime_data$month)
@@ -81,3 +81,5 @@ saveRDS(
 #### Save Fitted Data ####
 write_csv(combined_data,"data/02-analysis_data/fitted_calgary_crime.csv")
 write_parquet(combined_data,"data/02-analysis_data/fitted_calgary_crime.parquet")
+
+summary(crime_model)

### 2024-12-04 paper/paper.qmd
Implementation of the survey

@@
 fitted_data <- read_parquet(here("data/02-analysis_data/fitted_calgary_crime.parquet"))
+raw_data <- read_csv(here("data/01-raw_data/raw_data.csv"))
 ```
@@
 #| warning: false
-raw_data <- read_csv(here("data/01-raw_data/raw_data.csv"))
 
 # Get the column names of your raw data
-column_names <- colnames(raw_data)
-
-# Convert the column names to a data frame for kable
-column_df <- as.data.frame(column_names)
-
-# Display with kable
-kable(column_df)
+kable(head(raw_data))
 ```
@@
 
-# Idealized Methodology for Data Collection and Analysis{#sec-ideal-meth}
+# Idealized Methodology for Data Collection, Analysis and Survey{#sec-ideal-meth}
 
@@
 
-This section explores an idealized methodology for improving the quality and comprehensiveness of data collection and analysis for vehicle-related crimes in Calgary.
-While the current study relies on observational data, an ideal approach would incorporate advanced survey methodologies, improved sampling techniques, and simulations to address limitations in the existing dataset.
-This methodological framework can enhance the reliability of findings and strengthen the connection between crime trends and causal factors.
+The current Calgary crime dataset, while robust in capturing reported crimes, lacks contextual and unreported crime data that could enrich analyses.
+An idealized methodology involves supplementing this dataset with survey-based data collection to gather information about unreported crimes, public perceptions of safety, and crime-related behaviors.
+This approach bridges gaps in observational data and offers a more comprehensive view of crime dynamics in Calgary.
 
-## Survey Design and Data Collection
+Key goals of this methodology include:
 
-Comprehensive Crime Surveys:
+- Capturing unreported crimes to reduce underreporting bias.
 
-- Ideal Scenario: Conduct regular city-wide crime surveys that include questions about both reported and unreported vehicle-related crimes.
+- Understanding the demographic and socioeconomic contexts of crime victims.
 
-- Purpose: Current data likely underreports actual crime counts due to reliance on police-reported incidents. Surveys can capture unreported cases, providing a fuller picture of crime trends.
+- Providing actionable insights for law enforcement and policymakers.
 
-- Methodology: Use stratified random sampling to ensure representation from different neighborhoods, socioeconomic strata, and demographic groups.
+## Sampling Approach
 
-- Link to Literature: Surveys such as the British Crime Survey have demonstrated the value of incorporating unreported crimes into official statistics, highlighting disparities between reported and actual crime rates (Hough & Maxfield, 2007).
+Target Population:
 
-Integration with Citizen-Generated Data:
+- The target population includes Calgary residents aged 18 and above, distributed across all neighborhoods.
 
-- Ideal Scenario: Incorporate data from mobile applications or online platforms where citizens can anonymously report crimes.
+Stratified Random Sampling:
 
-- Purpose: Technology-driven reporting can supplement official data and improve coverage in areas with low reporting rates.
+- Stratification ensures that the sample reflects Calgary’s diverse population, accounting for factors like neighborhood, income levels, age, and gender.
 
-- Implementation: Partner with local governments to develop secure, user-friendly platforms.
+- Neighborhood-level stratification ensures that areas with low reporting rates are adequately represented.
 
-## Sampling Methodology
+Sample Size:
 
-Randomized Geospatial Sampling:
+- A sample of approximately 2,000 respondents is proposed to ensure statistical power and generalizability, accounting for Calgary’s population size and distribution.
 
-- Current Limitation: Observational data may over-represent areas with higher police presence or reporting infrastructure.
+Randomized Sampling:
 
-- Ideal Scenario: Implement geospatial sampling techniques to collect crime data evenly across Calgary, ensuring inclusion of underrepresented areas.
+- Respondents within each stratum are selected using random digit dialing for phone surveys or randomized email invitations for online surveys.
 
-- Simulation Study: Simulate different sampling scenarios to evaluate their impact on data completeness and spatial bias reduction.
+## Respondent Recruitment
 
-Temporal Sampling:
+Recruitment Strategy:
 
-- Current Limitation: Monthly aggregation in the dataset may mask short-term spikes or declines in crime activity.
+- ultimodal recruitment methods ensure inclusivity and accessibility:
+  - Phone Calls: For residents with landlines or mobile numbers.
+  - Online Platforms: Using email invitations and social media campaigns.
+  - In-Person Outreach: At community centers or local events, especially in neighborhoods with limited internet access.
 
-- Ideal Scenario: Collect daily or weekly data to capture finer temporal variations in crime trends.
+Incentives:
 
-- Example: A 2021 study on urban crime by Smith et al. showed that daily data improves the detection of time-sensitive factors like weather or public events.
+- Respondents are offered small incentives, such as gift cards or charitable donations on their behalf, to encourage participation.
+
+Inclusivity Measures:
+
+- Surveys are made available in multiple languages, reflecting Calgary’s linguistic diversity.
+Accessibility features, such as larger print and audio formats, are provided for individuals with disabilities.
+
+## Data Validation
+
+Verification of Responses:
+
+- Responses are cross-referenced with existing crime statistics where possible (e.g., verifying reported incidents through CPS records) to ensure consistency.
+
+- Duplicate or inconsistent responses are flagged and removed during preprocessing.
+
+Filtering Out Biases:
+
+- Screening questions are included to ensure respondents meet eligibility criteria (e.g., Calgary residency).
+
+- Statistical techniques, such as post-stratification weighting, are applied to align the sample distribution with Calgary’s population demographics.
+
+Handling Missing or Ambiguous Data:
+
+- Missing responses are minimized through mandatory fields for critical questions.
+Ambiguous responses are flagged for follow-up where feasible.
+
+## Survey Structure
+
+Sections and Topics:
+
+- Demographics: Age, gender, income, education level, and neighborhood of residence.
+Crime Experience: Details about reported and unreported crimes, including the type, timing, and location of incidents.
+
+- Perceptions of Safety: Questions on how safe respondents feel in their neighborhood and during specific times of the day.
+
+- Behavioral Insights: Questions on precautions taken to avoid crime (e.g., locking vehicles, using anti-theft devices).
+
+Question Types:
+
+- Closed-Ended Questions: For quantifiable data (e.g., “Have you ever been a victim of vehicle-related crime?”).
+
+- Likert Scales: To measure perceptions of safety and trust in law enforcement.
+
+- Open-Ended Questions: To allow respondents to share additional insights.
+
+Length and Accessibility:
+
+- The survey is designed to take no more than 15 minutes to complete, balancing depth of information with respondent engagement.
+
+## Implementation of The Survey: Calgary Vehicle-Related Crime and Safety Survey
+
+### Introduction
+
+Hello, and thank you for participating in this survey!
+Your responses will help us better understand vehicle-related crimes and public safety in Calgary.
+The survey will take approximately 10–15 minutes to complete.
+Your answers are anonymous, and all data will be used for research purposes only.
+
+### Section 1: Demographic Information
+
+* What is your age?
+  - Under 18
+  - 18–24
+  - 25–34
+  - 35–44
+  - 45–54
+  - 55–64
+  - 65 or older
+
+* What is your gender?
+  - Male
+  - Female
+  - Non-binary
+  - Prefer not to say
+
+* What is your highest level of education?
+  - Less than high school
+  - High school diploma or equivalent
+  - Some college/university
+  - Bachelor’s degree
+  - Graduate degree
+
+* What is your household income?
+  - Less than $30,000
+  - \$30,000 – \$59,999
+  - \$60,000 – \$99,999
+  - \$100,000 – \$149,999
+  - \$150,000 or more
+  - Prefer not to say
+
+* In which neighborhood of Calgary do you reside?
+  - (Dropdown menu of Calgary neighborhoods or a text field for manual entry)
+
+### Section 2: Crime Experience
+
+* Have you ever experienced vehicle-related crime in Calgary?
+  - Yes
+  - No
+
+* (If Yes) What type of vehicle-related crime did you experience? (Check all that apply)
+  - Theft FROM Vehicle (e.g., stolen items from inside or outside your car)
+  - Theft OF Vehicle (e.g., stolen car)
+  - Vandalism (e.g., broken windows, graffiti)
+
+* When did the most recent vehicle-related crime occur?
+  - Within the past month
+  - Within the past 6 months
+  - Within the past year
+  - More than a year ago
+
+* Did you report this incident to the Calgary Police Service?
+  - Yes
+  - No
+  - I’m not sure
+
+* (If No) Why didn’t you report the incident? (Check all that apply)
+  - It wasn’t serious enough
+  - I didn’t think the police could help
+  - I didn’t have time to report it
+  - I didn’t know how to report it
+  - Other (please specify): __________
 

### 2024-12-13 paper/paper.qmd
Revise the method for simulate data, correct some typo in paper

@@
 Among the several types of crimes, vehicle-related offenses include theft of vehicles and theft from vehicles remain a major issue in urban areas across the country[@rakauskas2009identification].
-These crimes disturb people's life but also burden local governments and law enforcement.
+These crimes disturb people's life but also burden local governments and law enforcement[@crawford2009urban].
 Over the years, Calgary, Canada, has seen varying patterns in vehicle-related crimes, which raises issues regarding future developments of these trends.
@@
 #| label: tbl-raw
-#| tbl-cap: Column Names of Raw Data
+#| tbl-cap: Column Names of Raw Data and first 6 rows of raw data
 #| echo: false
@@
 #| label: fig-combined-trend
-#| fig-cap: Trend of The Two Crime Combined
+#| fig-cap: Monthly trend of Theft FROM Vehicle and Theft OF Vehicle
 #| echo: false
@@
   labs(
-    title = "Trend of Theft FROM Vehicle and Theft OF Vehicle",
     x = "Time",
@@
 #| label: fig-year-trend
-#| tbl-cap: Trend of Crime Counts Over Years
+#| tbl-cap: Yearly trend of Theft FROM Vehicle and Theft OF Vehicle
 #| echo: false
@@
   labs(
-    title = "Trend of Crime Counts Over Years",
     x = "Year",
@@
 #| label: fig-forcast-trend
-#| fig-cap: Actual vs. Fitted Crime Trends (2018-2025)
+#| fig-cap: Comparison of actual crime count of Theft OF Vehicle and Theft FROM Vehicle and Fitted value
 #| echo: false
@@
   labs(
-    title = "Actual vs. Fitted Crime Trends (2018-2025)",
     x = "Time",
@@
 #| label: fig-residual-plot
-#| fig-cap: Residual Plot
+#| fig-cap: Residual again fitted plot
 #| echo: false

### 2024-12-13 scripts/00-simulate_data.R

@@ -14,14 +14,37 @@ library(tidyverse)
 set.seed(123)
 
 # Simulated data generation
+# Simulate basic structure of the dataset
 simulated_data <- data.frame(
-  Community = sample(c("01B", "02C", "03D", "04E"), size = 100, replace = TRUE),
-  Category = sample(c("Assault (Non-domestic)", "Break & Enter - Commercial", 
-                      "Break & Enter - Residential", "Theft", "Vandalism"), size = 100, replace = TRUE),
-  Crime.Count = sample(1:5, size = 100, replace = TRUE),
-  Year = sample(2019:2022, size = 100, replace = TRUE),
-  Month = sample(1:12, size = 100, replace = TRUE)
+  community = sample(c("01B", "02C", "03D", "04E"), size = 100, replace = TRUE),
+  year = sample(2019:2022, size = 100, replace = TRUE),
+  month = sample(1:12, size = 100, replace = TRUE)
 )
+
+# Assign crime categories based on community
+simulated_data$category <- ifelse(simulated_data$community == "01B", 
+                                  "Assault (Non-domestic)",
+                                  ifelse(simulated_data$community == "02C", 
+                                         "Break & Enter - Commercial",
+                                         ifelse(simulated_data$community == "03D", 
+                                                "Theft", 
+                                                "Vandalism")))
+
+# Assign crime counts with simple logic
+simulated_data$crime_count <- with(simulated_data, 
+                                   ifelse(year == 2019, 2, 
+                                          ifelse(year == 2020, 3, 
+                                                 ifelse(year == 2021, 4, 5))) + # Base count increases over years
+                                     ifelse(month %in% c(6, 7, 8), 2, 0) +    # Summer months get a boost
+                                     ifelse(category == "Theft", 2,           # Theft generally has higher counts
+                                            ifelse(category == "Break & Enter - Commercial", 1, 0))
+)
+
+# Cap the crime count for realism
+simulated_data$crime_count <- pmin(simulated_data$crime_count, 10)
+
+# View the first few rows
+head(simulated_data)
 
 #### Save data ####
 write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")

### 2024-12-13 paper/paper.qmd
Correct typos in paper

@@
 A Bayesian regression model is fit to historical crime data from January 2018 to October 2024, accounting for seasonal variations (months), long-term trends (years), and differences between crime categories.
-The usefulness of Bayesian modeling for crime trend forecasting is demonstrated by this analysis, providing law enforcement and policymakers practical insights to foresee and handle long-term and seasonal crime trends."
+The usefulness of Bayesian modeling for crime trend forecasting is demonstrated by this analysis, providing law enforcement and policymakers practical perception to foresee and handle long-term and seasonal crime trends."
 format: pdf
@@
 I created a Bayesian regression model to assess the effects of time (year and month) and crime category on reported crime counts using historical data spanning January 2018 through October 2024.
-Offering a comprehensive knowledge of how vehicle-related crimes have developed and may continue to alter in the near future, the model catches both long-term patterns and seasonal changes.
-The research also offers category-specific forecasts, therefore stressing variations in the seasonal and temporal trends of theft from and of vehicles.
+Offering a Thorough knowledge of how vehicle-related crimes have developed and may continue to alter in the near future, the model catches both long-term patterns and seasonal changes.
+The research also provides category-specific forecasts, therefore stressing variations in the seasonal and temporal trends of theft from and of vehicles.
 
-The analysis reveals a continued decline in vehicle-related crimes in Calgary, with a mean change of -60.5 each year, and notable mean differences of -454.8 between the two categories.
+The analysis discloses a continued decline in vehicle-related crimes in Calgary, with a mean change of -60.5 each year, and notable mean differences of -454.8 between the two categories.
 Theft from vehicles is anticipated to show cyclical surges in the summer months, indicating possible opportunistic habits.
@@
 The study is significant for its role in proactive crime prevention and resource optimization.
-This study offers precise and comprehensible forecasts, providing policymakers and law enforcement with evidence-based insights to inform decision-making.
-This study addresses a significant research gap and enhances public safety in Calgary.
+This study provides precise and comprehensible forecasts, providing policymakers and law enforcement with evidence-based perception to inform decision-making.
+This study addresses a significant research shortfall and enhances public safety in Calgary.
 
@@
 
-By understanding how this dataset measures real-world crime phenomena, we can more confidently interpret the insights and predictions derived from it.
+By understanding how this dataset measures real-world crime phenomena, we can more confidently interpret the perceptionand predictions derived from it.
 
@@
 #| label: tbl-cleaned-data
-#| tbl-cap: Head of cleaned Calgary Crime data 
+#| tbl-cap: Column Names and First 6 Rows of cleaned Calgary Crime data 
 #| echo: false
@@
 Interestingly, the mean crime count is 422.5, closely aligned with the median, suggesting a relatively symmetric distribution of the data.
-The interquartile range (IQR) spans from 361.2 (1st quartile) to 469.0 (3rd quartile), indicating that most monthly counts are concentrated within this range.
+The interquartile range (IQR) spans from 361.2 (1st quantile) to 469.0 (3rd quantile), indicating that most monthly counts are concentrated within this range.
 These figures highlight the scale and regularity of vehicle theft in Calgary and form an essential basis for analyzing and forecasting trends in such crimes.
@@
 
-The variable year represents the timeline over which the crime data is recorded, providing insight into how vehicle-related crime counts have changed annually.
+The variable year represents the timeline over which the crime data is recorded, providing perception into how vehicle-related crime counts have changed annually.
 By analyzing the data across different years, we can observe any long-term trends, such as consistent increases, decreases, or fluctuations in vehicle thefts.
@@
 Category distinguishes between "Theft FROM Vehicle" and "Theft OF Vehicle," allowing us to compare the frequency and patterns of these two crime types.
-Together, these variables highlight differences in the nature and timing of vehicle-related crimes, offering valuable insights into their temporal and categorical distributions.
+Together, these variables highlight differences in the nature and timing of vehicle-related crimes, offering useful perception into their temporal and categorical distributions.
 
@@
 #| label: fig-combined-trend
-#| fig-cap: Monthly trend of Theft FROM Vehicle and Theft OF Vehicle
+#| fig-cap: Monthly trend of Crime Count of Theft FROM Vehicle and Theft OF Vehicle Combined
 #| echo: false
@@
 By incorporating temporal and categorical variables, the model seeks to capture long-term trends, seasonal patterns, and differences between the two types of crimes.
-Ultimately, the model provides a foundation for projecting future crime rates, offering valuable insights that can support strategic decision-making and the development of targeted crime prevention initiatives for 2025 and beyond.
+Ultimately, the model provides a foundation for projecting future crime rates, offering useful perceptionthat can support strategic decision-making and the development of targeted crime prevention initiatives for 2025 and beyond.
 
@@
 #| label: fig-year-trend
-#| tbl-cap: Yearly trend of Theft FROM Vehicle and Theft OF Vehicle
+#| tbl-cap: Yearly Trend of Crime Count of Theft FROM Vehicle and Theft OF Vehicle Combined
 #| echo: false
@@
 The category variable differentiates between "Theft FROM Vehicle" and "Theft OF Vehicle," two distinct types of crimes with different characteristics and frequencies.
-This variable is crucial for explaining the variation in crime counts, as the two categories exhibit different trends over time and across months.
+This variable is essential for explaining the variation in crime counts, as the two categories exhibit different trends over time and across months.
 
@@
 
-The regression model estimates, summarized in the @tbl-model-summary below, provide insight into how predictors such as year, month, and category influence vehicle-related crime counts in Calgary.
+The regression model estimates, summarized in the @tbl-model-summary below, provide perception into how predictors such as year, month, and category influence vehicle-related crime counts in Calgary.
 The table includes coefficient estimates and their standard deviation to quantify the effect sizes and uncertainties associated with each predictor.
@@
 #| label: tbl-model-summary
-#| tbl-cap: Regression Estimates for Crime Counts
+#| tbl-cap: Regression Estimates of Coefficients and Standard Deviation for Crime Counts
 #| echo: false
@@
 By 2025, both categories are projected to experience reduced crime rates, with "Theft FROM Vehicle" showing a significant decrease in seasonal peaks and overall counts.
-These results offer valuable insights for law enforcement and policymakers, supporting the development of targeted strategies to maintain and accelerate these positive trends.
+These results offer useful Perception for law enforcement and policymakers, supporting the development of targeted strategies to maintain and accelerate these positive trends.
 
@@
 The model incorporates key predictors such as year, month, category, and their interactions to capture both temporal and categorical variations.
-The paper also provides forecasts for 2025, offering valuable insights into the expected future trends of these crimes.
+The paper also provides forecasts for 2025, offering useful Perception into the expected future trends of these crimes.
 
@@
 
-Another important insight is the fundamental difference between the two crime categories.
+Another important perception is the fundamental difference between the two crime categories.
 Theft FROM Vehicle is significantly more frequent than Theft OF Vehicle, and its seasonal variability is more pronounced.
@@
 
-A critical question arising from this research is how effective existing policy interventions have been in reducing vehicle-related crimes.
+A essential question arising from this research is how effective existing policy interventions have been in reducing vehicle-related crimes.
 While the model identifies a downward trend in both crime categories, it does not directly link these trends to specific policies, such as enhanced policing, public awareness campaigns, or technological improvements like vehicle immobilizers.
@@
 
-While the analysis provides valuable insights, it is not without limitations:
+While the analysis provides useful perception, it is not without limitations:
 
@@
 #| label: fig-residual-plot
-#| fig-cap: Residual again fitted plot
+#| fig-cap: Residual against fitted plot
 #| echo: false
@@
 An idealized methodology involves supplementing this dataset with survey-based data collection to gather information about unreported crimes, public perceptions of safety, and crime-related behaviors.
-This approach bridges gaps in observational data and offers a more comprehensive view of crime dynamics in Calgary.
 
@@
 
-- Providing actionable insights for law enforcement and policymakers.
+- Providing actionable perception for law enforcement and policymakers.
 
@@
 
-- Missing responses are minimized through mandatory fields for critical questions.
+- Missing responses are minimized through mandatory fields for essential questions.
 Ambiguous responses are flagged for follow-up where feasible.
@@
 
-- Behavioral Insights: Questions on precautions taken to avoid crime (e.g., locking vehicles, using anti-theft devices).
+- Behavioral Perception: Questions on precautions taken to avoid crime (e.g., locking vehicles, using anti-theft devices).
 
@@
 
-- Open-Ended Questions: To allow respondents to share additional insights.
+- Open-Ended Questions: To allow respondents to share additional perception.
 

### 2024-12-13 other/datasheet/datasheet.qmd
Rename datasheet_template.qmd to datasheet.qmd

---
title: "Datasheet for Community Crime Statistics"
author: 
  - Haobo Ren
thanks: "Code and data are available at: https://github.com/HaoboRrrr/calgary_vehicle_crime_forcast"
date: "29 November 2024"
format: pdf
number-sections: truejj
bibliography: references.bib
---

The raw dataset obtained from Open Data Calgary[@OpenCalgary] was recorded and updated monthly by the Calgary Police Service. The data is considered cumulative as late-reported incidents are often received well after an offence has occurred. An incident is either reported just after the crime happened, or reported on the Calgary Police Service[@calgarypolice].

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - This dataset was created to provide transparent and accessible crime statistics for the city of Calgary. It serves to inform the public, researchers, and policymakers about trends and patterns in various types of crimes, enabling evidence-based decision-making and fostering accountability.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset is maintained by Open Calgary, the City of Calgary’s open data platform. The data itself is collected and reported monthly by the Calgary Police Service (CPS).
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The funding for maintaining Open Calgary and its datasets is provided by the City of Calgary as part of its commitment to open data initiatives.
4. *Any other comments?*
    - The dataset reflects the City of Calgary's effort to increase public trust and foster collaboration through open data sharing.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each instance represents a monthly record of reported crimes in Calgary, categorized by crime type (e.g., "Theft FROM Vehicle," "Theft OF Vehicle") and broken down by specific counts.
2. *How many instances are there in total (of each type, if appropriate)?*
	- The dataset contains thousands of records spanning multiple years. Each record corresponds to a unique combination of a month, year, and crime type.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset aims to include all reported crimes as recorded by the Calgary Police Service. However, it may not account for unreported crimes, which could introduce a reporting bias.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance includes the following raw data fields: crime category, crime count, year, month, and a timestamp. These are sufficient for basic trend analysis and forecasting.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- The primary variable of interest is the crime count, which serves as the response variable in most analyses.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- The dataset does not include demographic information or contextual details such as socioeconomic factors, making it challenging to understand broader systemic influences on crime rates.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- Relationships between instances, such as trends across time or spatial groupings, are not directly represented but can be derived through analysis.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- While no official splits are provided, a common approach is to use early years for training predictive models and recent years for validation or testing.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- The dataset may contain reporting errors, such as inconsistent categorization of crimes. Additionally, some crimes might be double-counted due to human or system errors during data entry.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is self-contained and does not rely on external resources for its core data. However, external datasets (e.g., socioeconomic or geospatial data) may be required for advanced analyses.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No, the dataset does not contain personally identifiable or confidential information. It aggregates crime counts at the city level.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- Some users may find crime-related data distressing, especially if they are directly affected by the crimes reflected in the dataset.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- No explicit sub-populations are identified. The data is aggregated and does not include individual-level details.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, the dataset is fully anonymized and aggregated to prevent the identification of individuals.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- While crime data can be sensitive, this dataset avoids including personal or private information, focusing only on aggregate statistics.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- Each instance in the dataset represents reported crimes recorded by the Calgary Police Service (CPS). These reports are based on raw observational data, as police officers and administrative staff log crimes through official reporting systems. The data reflects the direct reporting of incidents, verified through CPS's internal processes to ensure accuracy before being released to the public.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The data was collected and processed using digital reporting systems employed by the Calgary Police Service. Officers log incidents into the CPS database, which categorizes them based on the type of crime and aggregates counts monthly. These systems undergo regular validation by CPS to ensure consistency in reporting and categorization. Open Calgary then publishes this data after further processing to remove any sensitive or identifiable information.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- This dataset is not a sample; it aims to include all reported crimes in Calgary. However, it does not account for unreported crimes, which means the dataset represents a subset of total crime incidents. As such, it is comprehensive for reported incidents but not necessarily representative of the true prevalence of crime in the city.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- The dataset relies on the efforts of Calgary Police Service officers and administrative staff. Their compensation comes through standard city employment contracts. Open Calgary staff curate the data for public use, ensuring it meets quality and accessibility standards.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The dataset includes monthly crime reports from 2018 to the present. Each instance is recorded close to the time of the incident, ensuring timeliness. Open Calgary updates the dataset on a regular basis, typically within a month of receiving the raw data from CPS.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No formal institutional review board (IRB) review was conducted, as the dataset only includes aggregated, anonymized data. However, Open Calgary follows standard practices for protecting privacy and ensuring compliance with ethical data-sharing guidelines.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was collected by the Calgary Police Service directly from reported incidents. Open Calgary acts as a third-party intermediary, curating and publishing the dataset on its open data platform.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- Since the data reflects incidents reported to the police, individuals filing reports are inherently aware that their information is being collected. However, the dataset itself is fully anonymized and does not retain identifiable personal details.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- By reporting crimes to the Calgary Police Service, individuals provide implied consent for their information to be used in law enforcement and administrative processes. No additional consent is required for inclusion in this anonymized and aggregated dataset.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- As the data is anonymized, individuals cannot revoke consent for its use once submitted. However, specific information associated with personal cases can be updated or removed if inaccuracies are reported to the Calgary Police Service.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No formal data protection impact analysis has been conducted. However, the dataset is designed to minimize risks to individuals by only including aggregate, anonymized statistics. This reduces the likelihood of any negative impact on the data subjects.
12. *Any other comments?*
	- The collection process for this dataset adheres to standard practices for public safety and transparency while prioritizing the privacy and confidentiality of individuals. The collaboration between the Calgary Police Service and Open Calgary ensures that the data is accurate, accessible, and responsibly shared.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, several preprocessing and cleaning steps were performed before the data was made publicly available on Open Calgary. These steps include:

Aggregation: Crime counts are aggregated monthly by crime type to ensure consistency and comparability across time.
Anonymization: Any personally identifiable information (e.g., addresses, names) is removed to protect individual privacy.
Standardization: Crime categories are standardized to ensure uniform classification across different data collection points.
Error Handling: Duplicates and obvious data entry errors (e.g., negative crime counts) are flagged and removed.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The raw data collected by the Calgary Police Service is maintained internally but is not publicly available. The processed dataset hosted by Open Calgary is a cleaned and aggregated version intended for public use. Access to the raw data may require special permissions and compliance with CPS’s privacy policies.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- The preprocessing of the data is managed internally by the Calgary Police Service and Open Calgary. While the exact tools used are not disclosed, similar tasks are typically handled using database management systems (e.g., SQL) and data cleaning tools. The publicly available dataset does not include software tools or scripts, but Open Calgary provides documentation for accessing and interpreting the data.
4. *Any other comments?*
	- The preprocessing steps focus on maintaining the usability and integrity of the dataset while prioritizing privacy and transparency. However, these steps may introduce limitations, such as the loss of granular details or contextual information, which could be valuable for more nuanced analyses.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Yes, the dataset has been used for various purposes, including:

Crime Trend Analysis: Researchers and policymakers have used the data to study historical crime trends in Calgary and assess the effectiveness of crime prevention measures.
Resource Allocation: Law enforcement agencies have utilized the data to allocate resources efficiently based on observed crime patterns.
Public Transparency: The dataset has been a key resource for increasing public awareness and understanding of crime dynamics in Calgary.
2. *What (other) tasks could the dataset be used for?*
	- The dataset has potential applications in a variety of tasks, including:

Predictive Modeling: Building machine learning models to forecast future crime trends.
Urban Planning: Informing urban development strategies by identifying high-crime areas.
Sociological Studies: Examining correlations between crime rates and socioeconomic or demographic variables.
Community Safety Programs: Designing targeted safety initiatives based on seasonal or geographic crime patterns.
3. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- Yes, the following aspects could impact future uses:

Aggregated Nature of Data: Since the data is aggregated by month and crime type, detailed analyses (e.g., hourly or neighborhood-level trends) are not possible.
Underreporting: The dataset includes only reported crimes, which may lead to underestimation of actual crime rates. This could bias analyses or decision-making if not accounted for.
Lack of Contextual Variables: The absence of socioeconomic or demographic data limits the ability to explore systemic factors influencing crime.
4. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- Yes, the dataset should not be used for:

Identifying Individuals: The data is anonymized and aggregated, making it inappropriate for any task attempting to identify individuals or specific incidents.
Definitive Cause-Effect Analysis: Without additional variables, the dataset cannot definitively establish causal relationships between crime rates and external factors.
5. *Any other comments?*
	- The dataset is a valuable resource for understanding crime trends, but users should approach its analysis thoughtfully, considering its limitations and potential biases. Open Calgary's ongoing updates and transparency efforts enhance its utility, but future improvements, such as geospatial details or additional contextual variables, could significantly expand its application scope.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, the dataset is freely available to the public through Open Calgary, which serves as the City of Calgary's open data platform. It is intended for use by researchers, policymakers, journalists, and the general public.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed through the Open Calgary website, where users can download it in multiple formats, such as CSV or Excel. Additionally, an API is provided for programmatic access to the data. As of now, the dataset does not have a digital object identifier (DOI).
3. *When will the dataset be distributed?*
	- The dataset has been publicly available on the Open Calgary platform since its creation. It is updated monthly as new crime data is collected and processed by the Calgary Police Service.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- Yes, the dataset is distributed under the Open Government License - Canada. This license allows users to copy, modify, and use the data for any purpose, provided that proper attribution is given to the City of Calgary and the Calgary Police Service. No fees or restrictions are associated with the use of this dataset under this license.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No third parties have imposed restrictions on this dataset. It is fully owned and managed by the City of Calgary and is made freely available to the public under the Open Government License.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No, there are no export controls or regulatory restrictions that apply to this dataset. It is freely accessible worldwide.
7. *Any other comments?*
	- The distribution model for this dataset ensures transparency and accessibility. The provision of both downloadable files and API access allows for flexible usage across different user types, from individual researchers to large-scale data applications.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset is hosted and maintained by Open Calgary, with data updates provided by the Calgary Police Service.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- For inquiries about the dataset, users can contact Open Calgary through their contact page or reach out to the Calgary Police Service for data-specific queries.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- Currently, there is no centralized erratum. Errors, if identified, are typically corrected in subsequent updates to the dataset.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Yes, the dataset is updated monthly with new crime reports. Updates are managed by Open Calgary in coordination with the Calgary Police Service, and changes are communicated through the Open Calgary platform.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- The dataset does not include personally identifiable information and is anonymized at the aggregation level. There are no specific retention limits, as the data represents aggregate statistics rather than individual records.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the dataset are not explicitly maintained but remain accessible through the Open Calgary platform. Users can retrieve historical records directly from the dataset's archive.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- There is no official mechanism for public contributions to the dataset. However, users are encouraged to share derivative works or insights publicly, provided they adhere to the Open Government License's attribution requirements. Any feedback or corrections can be submitted to Open Calgary for review.

8. *Any other comments?*
	- The maintenance and distribution strategy for this dataset reflects a commitment to open data principles. Continued collaboration between the Calgary Police Service and Open Calgary ensures its relevance and reliability for a wide range of applications.

\newpage

# References
